 
## Example 4 (ex4)                            


```{r}
ex4 <- fx.pre.field(loc.data = TRUE,
                               smalldist = 0.5,
                               width = c(2,2)) 

range = 2
pf <- ex4
mesh <- pf$mesh 
fem <- pf$mat 
barrier.triangles <- list(pf$bar1, pf$bar2)
loc.data <- pf$loc.data
poly.bar.orginal <- pf$poly.bar.orginal
poly.water <- pf$poly.water

zlim = c(0.1, 1)
xlim = poly.water@bbox[1, ] 
ylim = poly.water@bbox[2, ]

proj = inla.mesh.projector(mesh, xlim = xlim, 
                           ylim = ylim, dims=c(300, 300))

ggplot(data = pf$poly.water_sf) + 
      inlabru::gg(pf$mesh_h) + #plot mesh_hb alternatively
      geom_sf(data =pf$loc.data_sf,
          col='purple',size=1.7,alpha=0.5) 
```

### Choose two pair of points

One for each block with different r

```{r}
width <- 2
y.mid <- 5
y.up <- y.mid + (width/2)
y.low <- y.mid - (width/2)

location <- matrix(c(c(3.5, 6.5), rep(y.mid, 2)), ncol = 2)
```

```{r}
max.edge.length = 0.4
  
A <- list()
A[[1]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[1,1],y.up), nrow=1, ncol=2))
A[[2]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[1,1],(y.up + max.edge.length/2)), nrow=1, ncol=2))
A[[3]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[1,1],(y.up + max.edge.length)), nrow=1, ncol=2))

id.nodeA <- c()
id.nodeA[1] = which.max(A[[1]][1, ])
id.nodeA[2] = which.max(A[[2]][1, ])
id.nodeA[3] = which.max(A[[3]][1, ])

# just to check the coordinates and compare to the plot above
data.frame(x = c(mesh$loc[id.nodeA[1], 1], mesh$loc[id.nodeA[2], 1], mesh$loc[id.nodeA[3], 1]),
           y = c(mesh$loc[id.nodeA[1], 2], mesh$loc[id.nodeA[2], 2], mesh$loc[id.nodeA[3], 2]))

A.y.vector <- c(mesh$loc[id.nodeA[[1]],][2],
                  mesh$loc[id.nodeA[[2]],][2],
                  mesh$loc[id.nodeA[[3]],][2])

A.tmp <- A[[which(A.y.vector > y.up)[1]]]
id.node <- id.nodeA[which(A.y.vector > y.up)[1]]
id.coord <- c(mesh$loc[id.node, 1], mesh$loc[id.node, 2])
return.list.up <- list(A.tmp = A.tmp, id.coord = id.coord, id.node = id.node)

## lower point, i.e. point in barrier area
A <- list()
A[[1]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[1,1],y.up), nrow=1, ncol=2))
A[[2]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[1,1],(y.up - max.edge.length/2)), nrow=1, ncol=2))
A[[3]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[1,1],(y.up - max.edge.length)), nrow=1, ncol=2))
id.nodeA <- c()
id.nodeA[1] = which.max(A[[1]][1, ])
id.nodeA[2] = which.max(A[[2]][1, ])
id.nodeA[3] = which.max(A[[3]][1, ])

A.y.vector <- c(mesh$loc[id.nodeA[[1]],][2],
                  mesh$loc[id.nodeA[[2]],][2],
                  mesh$loc[id.nodeA[[3]],][2])

A.tmp <- A[[which(A.y.vector < y.up)[1]]]
id.node <- id.nodeA[which(A.y.vector < y.up)[1]]
id.coord <- c(mesh$loc[id.node, 1], mesh$loc[id.node, 2])

return.list.low <- list(A.tmp = A.tmp, id.coord = id.coord, id.node = id.node)

return.list <- list(normal.point = return.list.up, barrier.point = return.list.low)

coord.df_norm <- return.list$normal.point$id.coord
coord.df_bar <- return.list$barrier.point$id.coord

points_nb <- rbind(coord.df_norm, coord.df_bar)
rownames(points_nb) <- NULL
colnames(points_nb) <- c("x", "y")
points_nb <- as.matrix(points_nb)
poly_nb <- Polygon(points_nb)
SpatialPoints(poly_nb@coords)

sp_points_nb <- SpatialPoints(poly_nb@coords)
sf_points_nb <- st_as_sf(sp_points_nb)

ggplot(data = pf$poly.water_sf) + 
      inlabru::gg(pf$mesh) + #plot mesh_hb alternatively
      geom_sf(data =sf_points_nb,
          col='purple',size=1.7,alpha=0.5) 

ggplot(data = pf$poly.water_sf) + 
      inlabru::gg(pf$mesh) +
  geom_sf(data =sf_points_nb,
          col='purple',size=1.7,alpha=0.5) +
  ylim(c(4,6.5)) +
  xlim(c(2,5))

return.list.left <- return.list
coord.df_norm.left <- coord.df_norm
coord.df_bar.left <- coord.df_bar
```

```{r}
A <- list()
A[[1]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[2,1],y.up), nrow=1, ncol=2))
A[[2]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[2,1],(y.up + max.edge.length/2)), nrow=1, ncol=2))
A[[3]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[2,1],(y.up + max.edge.length)), nrow=1, ncol=2))

id.nodeA <- c()
id.nodeA[1] = which.max(A[[1]][1, ])
id.nodeA[2] = which.max(A[[2]][1, ])
id.nodeA[3] = which.max(A[[3]][1, ])

# just to check the coordinates and compare to the plot above
data.frame(x = c(mesh$loc[id.nodeA[1], 1], mesh$loc[id.nodeA[2], 1], mesh$loc[id.nodeA[3], 1]),
           y = c(mesh$loc[id.nodeA[1], 2], mesh$loc[id.nodeA[2], 2], mesh$loc[id.nodeA[3], 2]))

A.y.vector <- c(mesh$loc[id.nodeA[[1]],][2],
                  mesh$loc[id.nodeA[[2]],][2],
                  mesh$loc[id.nodeA[[3]],][2])

A.tmp <- A[[which(A.y.vector > y.up)[1]]]
id.node <- id.nodeA[which(A.y.vector > y.up)[1]]
id.coord <- c(mesh$loc[id.node, 1], mesh$loc[id.node, 2])
return.list.up <- list(A.tmp = A.tmp, id.coord = id.coord, id.node = id.node)

## lower point, i.e. point in barrier area
A <- list()
A[[1]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[2,1],y.up), nrow=1, ncol=2))
A[[2]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[2,1],(y.up - max.edge.length/2)), nrow=1, ncol=2))
A[[3]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[2,1],(y.up - max.edge.length)), nrow=1, ncol=2))
id.nodeA <- c()
id.nodeA[1] = which.max(A[[1]][1, ])
id.nodeA[2] = which.max(A[[2]][1, ])
id.nodeA[3] = which.max(A[[3]][1, ])

A.y.vector <- c(mesh$loc[id.nodeA[[1]],][2],
                  mesh$loc[id.nodeA[[2]],][2],
                  mesh$loc[id.nodeA[[3]],][2])

A.tmp <- A[[which(A.y.vector < y.up)[1]]]
id.node <- id.nodeA[which(A.y.vector < y.up)[1]]
id.coord <- c(mesh$loc[id.node, 1], mesh$loc[id.node, 2])

return.list.low <- list(A.tmp = A.tmp, id.coord = id.coord, id.node = id.node)

return.list <- list(normal.point = return.list.up, barrier.point = return.list.low)

coord.df_norm <- return.list$normal.point$id.coord
coord.df_bar <- return.list$barrier.point$id.coord

points_nb <- rbind(coord.df_norm, coord.df_bar)
rownames(points_nb) <- NULL
colnames(points_nb) <- c("x", "y")
points_nb <- as.matrix(points_nb)
poly_nb <- Polygon(points_nb)
SpatialPoints(poly_nb@coords)

sp_points_nb <- SpatialPoints(poly_nb@coords)
sf_points_nb <- st_as_sf(sp_points_nb)

ggplot(data = pf$poly.water_sf) + 
      inlabru::gg(pf$mesh) + #plot mesh_hb alternatively
      geom_sf(data =sf_points_nb,
          col='purple',size=1.7,alpha=0.5) 

ggplot(data = pf$poly.water_sf) + 
      inlabru::gg(pf$mesh) +
  geom_sf(data =sf_points_nb,
          col='purple',size=1.7,alpha=0.5) +
  ylim(c(4,6.5)) +
  xlim(c(5.5,7.5))

return.list.right <- return.list
coord.df_norm.right <- coord.df_norm
coord.df_bar.right <- coord.df_bar
```

### corr.from.Q function for two (or more) rb's

I need to calculate correlation for two points now, so pass a vector to solve instead of one Inode

```{r}
id.node <- list()
id.coord <- list()
in.id.node <- list()

id.node[[1]] = return.list.left$normal.point$id.node
id.node[[2]] = return.list.right$normal.point$id.node
id.coord[[1]] = return.list.left$normal.point$id.coord
id.coord[[2]] = return.list.right$normal.point$id.coord
in.id.node[[1]] = return.list.left$barrier.point$id.node
in.id.node[[2]] = return.list.right$barrier.point$id.node
```

### optim

```{r}
nb.model <- function(rbs, #rbs number of r_b
                     id.node = id.node, 
                     in.id.node = in.id.node) { 
  
  nb.model <- inla.barrier.pcmatern.plus(mesh, 
                             fem, 
                             barrier.triangles, 
                             prior.range,
                             prior.sigma,
                             range.fraction = rep(1, rbs))
  
  Q.nb <- inla.rgeneric.q(nb.model, "Q", 
                          theta = c(log(prior.sigma[1]), log(prior.range[1])))
  
  corr.nb <- 
    corr.from.Q.alltogether(Q = Q.nb,
                            id.node = id.node,
                            in.id.node = in.id.node)
  
  return(list(nb.model = nb.model, Q = Q.nb, corr = corr.nb))
}


find.aimed.ratios_ <- function(x, 
                               aimed.ratio,
                               corr.nb) {
  
  barrier.model <- inla.barrier.pcmatern.plus(
    mesh = mesh,
    fem = fem,
    barrier.triangles = barrier.triangles,
    prior.range = prior.range,
    prior.sigma = prior.sigma,
    range.fraction = x)
  
  Q <- inla.rgeneric.q(
    barrier.model, 
    "Q",
    theta = c(log(prior.sigma[1]), 
              log(prior.range[1])))
  
  corr.bm <- corr.from.Q.alltogether(
    Q = Q, 
    id.node = id.node, 
    in.id.node = in.id.node)
  
  corr <- c()
  for (i in seq_along(corr.bm)) {
    corr[i] <- corr.bm[[i]]/corr.nb[[i]]
  }
  
  A <- diag(aimed.ratio, nrow = length(aimed.ratio))
  B <- diag(corr, nrow = length(corr))
  M <- A-B
  mini <- norm(M, "F")
  
  return(mini)
}

## with corr nb = 1
par = rep(0.5, length(aim))
optim(par = par, find.aimed.ratios_, 
      aimed.ratio = aim, corr.nb = list(1,1),
      method="L-BFGS-B",
      lower = c(0.01, 0.01), 
      upper = c(1,1))
```

$par: [1] 0.1174683 0.1075167
$value: [1] 1.300353e-05
$counts: function gradient 
      41       41 
$convergence: [1] 0
$message: [1] "CONVERGENCE: REL_REDUCTION_OF_F <= FACTR*EPSMCH"

```{r}
## with corr nb = corr.ref
corr.ref <- nb.model(rbs = 2, id.node = id.node, in.id.node = in.id.node)$corr
optim(par = par, find.aimed.ratios_, 
      aimed.ratio = aim, corr.nb = corr.ref,
      method="L-BFGS-B",
      lower = c(0.01, 0.01), 
      upper = c(1,1))
```

$par: [1] 0.1157458 0.1071045
$value: [1] 1.781817e-06
$counts: function gradient 
      30       30 
$convergence: [1] 0
$message: [1] "CONVERGENCE: REL_REDUCTION_OF_F <= FACTR*EPSMCH"

### Barrier model considering the prev. results

Comparison barrier model and stationary model, using the range fraction obtained from `optim` for the barrier model.

#### Simulate response variable

```{r}
r_nbT <- 2
r_bT <- c(0.1, 0.1) 
df.T <- trans.generate.q2(mesh = mesh, fem = fem, 
                        loc.data = loc.data, 
                        set.inla.seed = 1702, 
                        barrier.triangles = barrier.triangles, 
                        prior.range = c(2, 0.5), prior.sigma = c(1, 0.1),
                        range.fraction = c(r_bT[1],r_bT[2]), 
                        range = r_nbT,
                        sigma.u = 1, sigma.epsilon = 0.2,
                        return.list = TRUE)


df <- df.T$list.field$df
A.data <- df.T$list.field$A.data
```

#### Stationary model

```{r}
prior.range.st = c(1, 0.5)
prior.sigma.st = c(1, 0.1)

stk <- inla.stack(data=list(y=df$y), 
                    A=list(A.data, 1),
                    effects=list(s=1:mesh$n, 
                                 intercept=rep(1, nrow(df))), 
                    remove.unused = FALSE, 
                    tag='est')
 
model.stat <- inla.spde2.pcmatern(mesh, 
                                  prior.range = 
                                    c(prior.range.st[1],
                                      prior.range.st[2]),
                                  prior.sigma = 
                                    c(prior.sigma.st[1],
                                      prior.sigma.st[2]))
  
formula.st <- y ~ 0 + intercept + f(s, model=model.stat)
  
res.stationary <- inla(formula.st, data=inla.stack.data(stk),
            control.predictor=list(A = inla.stack.A(stk)),
            family = 'gaussian',
            control.family = list(hyper = list(prec = list(
              prior = "pc.prec", fixed = FALSE, 
              param = c(0.2,0.5)))),
            control.mode=list(restart=T, theta=c(4,-1.7,0.25)))
  
res.stationary$summary.hyperpar
```

#### Transparent Barrier model with reference correlation not 1

```{r}
## range fraction optim line 323
x <- c(0.1157458, 0.1071045)
barrier.model <- inla.barrier.pcmatern.plus(mesh, 
                             fem, 
                             barrier.triangles, 
                             prior.range = c(1, 0.5),
                             prior.sigma = c(1, 0.1),
                             range.fraction = c(x[1],x[2]))

formula <- y ~ 0 + intercept + f(s, model = barrier.model)

res.barrier <- inla(formula, 
                    data = inla.stack.data(stk),
                    control.predictor = 
                      list(A = inla.stack.A(stk)),
                    family = 'gaussian',
                    control.family = 
                      list(hyper = list(
                          prec = list(prior = "pc.prec", 
                                      fixed = FALSE, 
                                      param = c(0.2,0.5)))),
                    control.mode=list(restart=T, 
                                      theta=c(3.2, 0.4, 1.6)))
  
exp(res.barrier$summary.hyperpar) 
```

## Discussion

Results from the model are similar, however the confidence interval for the range hyperparameter in the Transparent Barrier model is narrower.








