## Example 5

Spatial domain: rectangle
Barrier: square inside rect.

```{r}
range = 2
max.edge.length <- 0.4
set.inla.seed <- 2303
n <- 20

poly1 <- local.square.polygon(xlim = c(4,6), ylim = c(4,6))
poly.original <- SpatialPolygons(poly1@polygons)

loc1 <- matrix(c(0,0, 10,0, 0,10, 10,10), 4, 2, byrow = T)

seg <- inla.sp2segment(poly.original)

mesh <- inla.mesh.2d(loc=loc1, interior = seg, 
                    max.e = max.edge.length, offset=1)

tl <- length(mesh$graph$tv[,1])
# - the number of triangles in the mesh
posTri <- matrix(0, tl, 2)

for (t in 1:tl){
  temp = mesh$loc[mesh$graph$tv[t, ], ]
  posTri[t,] = colMeans(temp)[c(1,2)] 
}
posTri <- SpatialPoints(posTri)

bar.original <- over(poly.original, SpatialPoints(posTri), returnList=T)
bar.original <- unlist(bar.original)
poly.bar.orginal <- inla.barrier.polygon(mesh, barrier.triangles = bar.original)

# BARRIER 1 = poly.original
bar1 <- over(poly1, SpatialPoints(posTri), returnList=T)
bar1 <- unlist(bar1)
poly.bar1 <- inla.barrier.polygon(mesh, barrier.triangles = bar1)

#sum(bar1==bar.original) == length(bar1)

mat <-  inla.barrier.fem.plus(mesh, list(bar1))

xlim=c(4, 6)
ylim=c(4, 6)

xlim = range(xlim)
ylim = range(ylim)

corner1 = c(xlim[1], ylim[2])
corner2 = c(xlim[2], ylim[1])

poly1_h = Polygon(rbind(corner1, c(corner1[1], corner2[2]), corner2, c(corner2[1], corner1[2]), corner1), hole = TRUE)

loc1 <- matrix(c(2,2, 8,2, 8,8, 2,8), 4, 2, byrow = T)

locp <- Polygon(loc1, hole = FALSE)
    
poly.water <- SpatialPolygons(list(Polygons(list(locp, poly1_h), '0')))
poly.water_sf <- st_as_sf(poly.water)

set.seed(set.inla.seed)
loc.data <- spsample(x = poly.water, n = n, type = "random")
loc.data_sf <- st_as_sf(loc.data)
loc.data <- loc.data@coords

mesh_h <-inla.mesh.2d(boundary = poly.water_sf,
                      max.e = max.edge.length, 
                      offset=1)

fem <- mat 
barrier.triangles <- list(bar1)

zlim = c(0.1, 1)
xlim = poly.water@bbox[1, ] 
ylim = poly.water@bbox[2, ]

proj = inla.mesh.projector(mesh, xlim = xlim, 
                           ylim = ylim, dims=c(300, 300))

ggplot(data = poly.water_sf) + 
      inlabru::gg(mesh_h) + 
      geom_sf(data =loc.data_sf,
          col='purple',size=1.7,alpha=0.5) 
```
```{r}
width <- 2 #in this case width in y and x is the same
y.mid <- 5
y.up <- y.mid + (width/2)
y.low <- y.mid - (width/2)

x.mid <- 5
x.right <- x.mid + (width/2)
x.left <- x.mid - (width/2)

location <- matrix(c(c(5, x.mid), c(y.mid, 5)), ncol = 2)
```

```{r}
# pair of points for top side of the barrier
# x = 5, and I want to find the coordinates of the points on the y axis

A <- list()
A[[1]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[1,1],y.up), nrow=1, ncol=2))
A[[2]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[1,1],(y.up + max.edge.length/2)), nrow=1, ncol=2))
A[[3]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[1,1],(y.up + max.edge.length)), nrow=1, ncol=2))

id.nodeA <- c()
id.nodeA[1] = which.max(A[[1]][1, ])
id.nodeA[2] = which.max(A[[2]][1, ])
id.nodeA[3] = which.max(A[[3]][1, ])

# just to check the coordinates and compare to the plot above
data.frame(x = c(mesh$loc[id.nodeA[1], 1], mesh$loc[id.nodeA[2], 1], mesh$loc[id.nodeA[3], 1]),
           y = c(mesh$loc[id.nodeA[1], 2], mesh$loc[id.nodeA[2], 2], mesh$loc[id.nodeA[3], 2]))

A.y.vector <- c(mesh$loc[id.nodeA[[1]],][2],
                  mesh$loc[id.nodeA[[2]],][2],
                  mesh$loc[id.nodeA[[3]],][2])

A.tmp <- A[[which(A.y.vector > y.up)[1]]]
id.node <- id.nodeA[which(A.y.vector > y.up)[1]]
id.coord <- c(mesh$loc[id.node, 1], mesh$loc[id.node, 2])
return.list.up <- list(A.tmp = A.tmp, id.coord = id.coord, id.node = id.node)

## lower point, i.e. point in barrier area
A <- list()
A[[1]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[1,1],y.up), nrow=1, ncol=2))
A[[2]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[1,1],(y.up - max.edge.length/2)), nrow=1, ncol=2))
A[[3]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[1,1],(y.up - max.edge.length)), nrow=1, ncol=2))
id.nodeA <- c()
id.nodeA[1] = which.max(A[[1]][1, ])
id.nodeA[2] = which.max(A[[2]][1, ])
id.nodeA[3] = which.max(A[[3]][1, ])

A.y.vector <- c(mesh$loc[id.nodeA[[1]],][2],
                  mesh$loc[id.nodeA[[2]],][2],
                  mesh$loc[id.nodeA[[3]],][2])

A.tmp <- A[[which(A.y.vector < y.up)[1]]]
id.node <- id.nodeA[which(A.y.vector < y.up)[1]]
id.coord <- c(mesh$loc[id.node, 1], mesh$loc[id.node, 2])

return.list.low <- list(A.tmp = A.tmp, id.coord = id.coord, id.node = id.node)

return.list <- list(normal.point = return.list.up, barrier.point = return.list.low)

coord.df_norm <- return.list$normal.point$id.coord
coord.df_bar <- return.list$barrier.point$id.coord

points_nb <- rbind(coord.df_norm, coord.df_bar)
rownames(points_nb) <- NULL
colnames(points_nb) <- c("x", "y")
points_nb <- as.matrix(points_nb)
poly_nb <- Polygon(points_nb)
SpatialPoints(poly_nb@coords)

sp_points_nb <- SpatialPoints(poly_nb@coords)
sf_points_nb <- st_as_sf(sp_points_nb)

ggplot(data = poly.water_sf) + 
      inlabru::gg(mesh) + #plot mesh_hb alternatively
      geom_sf(data =sf_points_nb,
          col='purple',size=1.7,alpha=0.5) 

ggplot(data = poly.water_sf) + 
      inlabru::gg(mesh) +
  geom_sf(data =sf_points_nb,
          col='purple',size=1.7,alpha=0.5) +
  ylim(c(5,7)) +
  xlim(c(4,6))

return.list.top <- return.list
coord.df_norm.top <- coord.df_norm
coord.df_bar.top <- coord.df_bar
```

```{r}
# pair of points for left side of the barrier
# y = 5, and I want to find the coordinates of the points on the x axis

# x.left + ... is barrier area, and x.left -... is normal area
# point inside the barrier area
A <- list()
A[[1]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(x.left, location[2,2]), nrow=1, ncol=2))
A[[2]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c((x.left + max.edge.length/2), location[2,2]), nrow=1, ncol=2))
A[[3]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c((x.left + max.edge.length), location[2,2]), nrow=1, ncol=2))

id.nodeA <- c()
id.nodeA[1] = which.max(A[[1]][1, ])
id.nodeA[2] = which.max(A[[2]][1, ])
id.nodeA[3] = which.max(A[[3]][1, ])

# just to check the coordinates and compare to the plot above
data.frame(x = c(mesh$loc[id.nodeA[1], 1], mesh$loc[id.nodeA[2], 1], mesh$loc[id.nodeA[3], 1]),
           y = c(mesh$loc[id.nodeA[1], 2], mesh$loc[id.nodeA[2], 2], mesh$loc[id.nodeA[3], 2]))

A.x.vector <- c(mesh$loc[id.nodeA[[1]],][1],
                  mesh$loc[id.nodeA[[2]],][1],
                  mesh$loc[id.nodeA[[3]],][1])

A.tmp <- A[[which(A.x.vector > x.left)[1]]]
id.node <- id.nodeA[which(A.x.vector > x.left)[1]]
id.coord <- c(mesh$loc[id.node, 1], mesh$loc[id.node, 2])
return.list.up <- list(A.tmp = A.tmp, id.coord = id.coord, id.node = id.node)
# up on the x axis

## point in normal area
A <- list()
A[[1]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(x.left, location[2,2]), nrow=1, ncol=2))
A[[2]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c((x.left - max.edge.length/2), location[2,2]), nrow=1, ncol=2))
A[[3]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c((x.left - max.edge.length), location[2,2]), nrow=1, ncol=2))
id.nodeA <- c()
id.nodeA[1] = which.max(A[[1]][1, ])
id.nodeA[2] = which.max(A[[2]][1, ])
id.nodeA[3] = which.max(A[[3]][1, ])

# just to check the coordinates and compare to the plot above
data.frame(x = c(mesh$loc[id.nodeA[1], 1], mesh$loc[id.nodeA[2], 1], mesh$loc[id.nodeA[3], 1]),
           y = c(mesh$loc[id.nodeA[1], 2], mesh$loc[id.nodeA[2], 2], mesh$loc[id.nodeA[3], 2]))

A.x.vector <- c(mesh$loc[id.nodeA[[1]],][1],
                  mesh$loc[id.nodeA[[2]],][1],
                  mesh$loc[id.nodeA[[3]],][1])

A.tmp <- A[[which(A.x.vector < x.left)[1]]]
id.node <- id.nodeA[which(A.x.vector < x.left)[1]]
id.coord <- c(mesh$loc[id.node, 1], mesh$loc[id.node, 2])

return.list.low <- list(A.tmp = A.tmp, id.coord = id.coord, id.node = id.node)
```


```{r}
return.list <- list(normal.point = return.list.low, barrier.point = return.list.up)

coord.df_norm <- return.list$normal.point$id.coord
coord.df_bar <- return.list$barrier.point$id.coord

points_nb <- rbind(coord.df_norm, coord.df_bar)
rownames(points_nb) <- NULL
colnames(points_nb) <- c("x", "y")
points_nb <- as.matrix(points_nb)
poly_nb <- Polygon(points_nb)
SpatialPoints(poly_nb@coords)

sp_points_nb <- SpatialPoints(poly_nb@coords)
sf_points_nb <- st_as_sf(sp_points_nb)

ggplot(data = poly.water_sf) + 
      inlabru::gg(mesh) + #plot mesh_hb alternatively
      geom_sf(data =sf_points_nb,
          col='purple',size=1.7,alpha=0.5) 

ggplot(data = poly.water_sf) + 
      inlabru::gg(mesh) +
  geom_sf(data =sf_points_nb,
          col='purple',size=1.7,alpha=0.5) +
  ylim(c(4,6)) +
  xlim(c(3,5))

return.list.left <- return.list
coord.df_norm.left <- coord.df_norm
coord.df_bar.left <- coord.df_bar

id.node <- list()
id.coord <- list()
in.id.node <- list()

id.node[[1]] = return.list.top$normal.point$id.node
id.node[[2]] = return.list.left$normal.point$id.node
id.coord[[1]] = return.list.top$normal.point$id.coord
id.coord[[2]] = return.list.left$normal.point$id.coord
in.id.node[[1]] = return.list.top$barrier.point$id.node
in.id.node[[2]] = return.list.left$barrier.point$id.node
```

### optim

**top side**

```{r}
prior.range = c(1, 0.5)
prior.sigma = c(1, 0.1)

id.node = id.node[[1]]
in.id.node = in.id.node[[1]]

nb.model <- function(rbs, #rbs number of r_b
                     id.node = id.node, 
                     in.id.node = in.id.node) { 
  
  nb.model <- inla.barrier.pcmatern.plus(mesh, 
                             fem, 
                             barrier.triangles, 
                             prior.range,
                             prior.sigma,
                             range.fraction = rep(1, rbs))
  
  Q.nb <- inla.rgeneric.q(nb.model, "Q", 
                          theta = c(log(prior.sigma[1]), log(prior.range[1])))
  
  corr.nb <- 
    corr.from.Q.alltogether(Q = Q.nb,
                            id.node = id.node,
                            in.id.node = in.id.node)
  
  return(list(nb.model = nb.model, Q = Q.nb, corr = corr.nb))
}

corr.nb <- nb.model(rbs = 1,
                    id.node = id.node, 
                    in.id.node = in.id.node)$corr

find.aimed.ratios_ <- function(x, 
                               aimed.ratio,
                               corr.nb) {
  
  barrier.model <- inla.barrier.pcmatern.plus(
    mesh = mesh,
    fem = fem,
    barrier.triangles = barrier.triangles,
    prior.range = prior.range,
    prior.sigma = prior.sigma,
    range.fraction = x)
  
  Q <- inla.rgeneric.q(
    barrier.model, 
    "Q",
    theta = c(log(prior.sigma[1]), 
              log(prior.range[1])))
  
  corr.bm <- corr.from.Q.alltogether(
    Q = Q, 
    id.node = id.node, 
    in.id.node = in.id.node)
  
  corr <- c()
  for (i in seq_along(corr.bm)) {
    corr[i] <- corr.bm[[i]]/corr.nb[[i]]
  }
  
  A <- diag(aimed.ratio, nrow = length(aimed.ratio))
  B <- diag(corr, nrow = length(corr))
  M <- A-B
  mini <- norm(M, "F")
  
  return(mini)
}

## with corr nb = 1
aim = 0.5
par = rep(0.5, length(aim))
optim(par = par, find.aimed.ratios_, 
      aimed.ratio = aim, corr.nb = 1,
      method="L-BFGS-B",
      lower = 0.01, 
      upper = 1)
```

$par: [1] 1
$value: [1] 0.2032115
$counts: function gradient 
       3        3 
$convergence: [1] 0
$message: [1] "CONVERGENCE: NORM OF PROJECTED GRADIENT <= PGTOL"

```{r}
optim(par = par, find.aimed.ratios_, 
      aimed.ratio = aim, corr.nb = corr.nb,
      method="L-BFGS-B",
      lower = 0.01, 
      upper = 1)
```

$par: [1] 0.4792988
$value: [1] 1.363331e-06
$counts: function gradient 
      43       43 
$convergence: [1] 0
$message: [1] "CONVERGENCE: REL_REDUCTION_OF_F <= FACTR*EPSMCH"

#### more optim for this particular case

```{r}
find.aimed.ratios_(x=1, aimed.ratio = aim, corr.nb = 1) #0.2032115
find.aimed.ratios_(x=0.9, aimed.ratio = aim, corr.nb = 1) #0.2208985
find.aimed.ratios_(x=0.1, aimed.ratio = aim, corr.nb = 1) #0.5622385

aim = 0.2
optim(par = par, find.aimed.ratios_, 
      aimed.ratio = aim, corr.nb = 1,
      method="L-BFGS-B",
      lower = 0.01, 
      upper = 1)

aim = 0.7
optim(par = par, find.aimed.ratios_, 
      aimed.ratio = aim, corr.nb = 1,
      method="L-BFGS-B",
      lower = 0.01, 
      upper = 1)
```

**left side**

```{r}
prior.range = c(1, 0.5)
prior.sigma = c(1, 0.1)

id.node = id.node[[2]]
in.id.node = in.id.node[[2]]

nb.model <- function(rbs, #rbs number of r_b
                     id.node = id.node, 
                     in.id.node = in.id.node) { 
  
  nb.model <- inla.barrier.pcmatern.plus(mesh, 
                             fem, 
                             barrier.triangles, 
                             prior.range,
                             prior.sigma,
                             range.fraction = rep(1, rbs))
  
  Q.nb <- inla.rgeneric.q(nb.model, "Q", 
                          theta = c(log(prior.sigma[1]), log(prior.range[1])))
  
  corr.nb <- 
    corr.from.Q.alltogether(Q = Q.nb,
                            id.node = id.node,
                            in.id.node = in.id.node)
  
  return(list(nb.model = nb.model, Q = Q.nb, corr = corr.nb))
}

corr.nb <- nb.model(rbs = 1,
                    id.node = id.node, 
                    in.id.node = in.id.node)$corr

find.aimed.ratios_ <- function(x, 
                               aimed.ratio,
                               corr.nb) {
  
  barrier.model <- inla.barrier.pcmatern.plus(
    mesh = mesh,
    fem = fem,
    barrier.triangles = barrier.triangles,
    prior.range = prior.range,
    prior.sigma = prior.sigma,
    range.fraction = x)
  
  Q <- inla.rgeneric.q(
    barrier.model, 
    "Q",
    theta = c(log(prior.sigma[1]), 
              log(prior.range[1])))
  
  corr.bm <- corr.from.Q.alltogether(
    Q = Q, 
    id.node = id.node, 
    in.id.node = in.id.node)
  
  corr <- c()
  for (i in seq_along(corr.bm)) {
    corr[i] <- corr.bm[[i]]/corr.nb[[i]]
  }
  
  A <- diag(aimed.ratio, nrow = length(aimed.ratio))
  B <- diag(corr, nrow = length(corr))
  M <- A-B
  mini <- norm(M, "F")
  
  return(mini)
}

## with corr nb = 1
aim = 0.5
par = rep(0.5, length(aim))
optim(par = par, find.aimed.ratios_, 
      aimed.ratio = aim, corr.nb = 1,
      method="L-BFGS-B",
      lower = 0.01, 
      upper = 1)
```

$par: [1] 1
$value: [1] 0.2137368
$counts: function gradient 
       3        3 
$convergence: [1] 0
$message: [1] "CONVERGENCE: NORM OF PROJECTED GRADIENT <= PGTOL"

```{r}
optim(par = par, find.aimed.ratios_, 
      aimed.ratio = aim, corr.nb = corr.nb,
      method="L-BFGS-B",
      lower = 0.01, 
      upper = 1)
```

$par: [1] 0.4765782
$value: [1] 1.397526e-06


### Barrier model considering the prev. results

Comparison barrier model and stationary model, using the range fraction obtained from `optim` for the barrier model.

**range for the normal area = 1**

```{r}
r_nbT <- 1
r_bT <- c(0.5) 
df.T <- trans.generate.q2(mesh = mesh, fem = fem, 
                        loc.data = loc.data, 
                        set.inla.seed = 2303, 
                        barrier.triangles = barrier.triangles, 
                        prior.range = c(1, 0.5), prior.sigma = c(1, 0.1),
                        range.fraction = c(r_bT[1]), 
                        range = r_nbT,
                        sigma.u = 1, sigma.epsilon = 0.2,
                        return.list = TRUE)


df <- df.T$list.field$df
A.data <- df.T$list.field$A.data


#### Stationary model
prior.range.st = c(1, 0.5)
prior.sigma.st = c(1, 0.1)

stk <- inla.stack(data=list(y=df$y), 
                    A=list(A.data, 1),
                    effects=list(s=1:mesh$n, 
                                 intercept=rep(1, nrow(df))), 
                    remove.unused = FALSE, 
                    tag='est')
 
model.stat <- inla.spde2.pcmatern(mesh, 
                                  prior.range = 
                                    c(prior.range.st[1],
                                      prior.range.st[2]),
                                  prior.sigma = 
                                    c(prior.sigma.st[1],
                                      prior.sigma.st[2]))
  
formula.st <- y ~ 0 + intercept + f(s, model=model.stat)
  
res.stationary <- inla(formula.st, data=inla.stack.data(stk),
            control.predictor=list(A = inla.stack.A(stk)),
            family = 'gaussian',
            control.family = list(hyper = list(prec = list(
              prior = "pc.prec", fixed = FALSE, 
              param = c(0.2,0.5)))),
            control.mode=list(restart=T, theta=c(4,-1.7,0.25)))
  
#### Transparent Barrier model with reference correlation not 1
## range fraction optim line 507
x <- 0.4792988
barrier.model <- inla.barrier.pcmatern.plus(mesh, 
                             fem, 
                             barrier.triangles, 
                             prior.range = c(1, 0.5),
                             prior.sigma = c(1, 0.1),
                             range.fraction = c(x[1]))

formula <- y ~ 0 + intercept + f(s, model = barrier.model)

res.barrier <- inla(formula, 
                    data = inla.stack.data(stk),
                    control.predictor = 
                      list(A = inla.stack.A(stk)),
                    family = 'gaussian',
                    control.family = 
                      list(hyper = list(
                          prec = list(prior = "pc.prec", 
                                      fixed = FALSE, 
                                      param = c(0.2,0.5)))),
                    control.mode=list(restart=T, 
                                      theta=c(3.2, 0.4, 1.6)))
  
res.stationary$summary.hyperpar
exp(res.barrier$summary.hyperpar) 
```

**range for the normal area = 2**

```{r}
r_nbT <- 2
r_bT <- c(0.5) 
df.T <- trans.generate.q2(mesh = mesh, fem = fem, 
                        loc.data = loc.data, 
                        set.inla.seed = 2303, 
                        barrier.triangles = barrier.triangles, 
                        prior.range = c(1, 0.5), prior.sigma = c(1, 0.1),
                        range.fraction = c(r_bT[1]), 
                        range = r_nbT,
                        sigma.u = 1, sigma.epsilon = 0.2,
                        return.list = TRUE)


df <- df.T$list.field$df
A.data <- df.T$list.field$A.data


#### Stationary model
prior.range.st = c(1, 0.5)
prior.sigma.st = c(1, 0.1)

stk <- inla.stack(data=list(y=df$y), 
                    A=list(A.data, 1),
                    effects=list(s=1:mesh$n, 
                                 intercept=rep(1, nrow(df))), 
                    remove.unused = FALSE, 
                    tag='est')
 
model.stat <- inla.spde2.pcmatern(mesh, 
                                  prior.range = 
                                    c(prior.range.st[1],
                                      prior.range.st[2]),
                                  prior.sigma = 
                                    c(prior.sigma.st[1],
                                      prior.sigma.st[2]))
  
formula.st <- y ~ 0 + intercept + f(s, model=model.stat)
  
res.stationary <- inla(formula.st, data=inla.stack.data(stk),
            control.predictor=list(A = inla.stack.A(stk)),
            family = 'gaussian',
            control.family = list(hyper = list(prec = list(
              prior = "pc.prec", fixed = FALSE, 
              param = c(0.2,0.5)))),
            control.mode=list(restart=T, theta=c(4,-1.7,0.25)))
  
#### Transparent Barrier model with reference correlation not 1
## range fraction optim line 507
x <- 0.4792988
barrier.model <- inla.barrier.pcmatern.plus(mesh, 
                             fem, 
                             barrier.triangles, 
                             prior.range = c(1, 0.5),
                             prior.sigma = c(1, 0.1),
                             range.fraction = c(x[1]))

formula <- y ~ 0 + intercept + f(s, model = barrier.model)

res.barrier <- inla(formula, 
                    data = inla.stack.data(stk),
                    control.predictor = 
                      list(A = inla.stack.A(stk)),
                    family = 'gaussian',
                    control.family = 
                      list(hyper = list(
                          prec = list(prior = "pc.prec", 
                                      fixed = FALSE, 
                                      param = c(0.2,0.5)))),
                    control.mode=list(restart=T, 
                                      theta=c(3.2, 0.4, 1.6)))
  
res.stationary$summary.hyperpar
exp(res.barrier$summary.hyperpar) 
```

**range for the normal area = 4**

```{r}
#### Simulate response variable for loc.data
r_nbT <- 4
r_bT <- c(0.5)
df.T <- trans.generate.q2(mesh = mesh, fem = fem, 
                        loc.data = loc.data, 
                        set.inla.seed = 2303, 
                        barrier.triangles = barrier.triangles, 
                        prior.range = c(1, 0.5), prior.sigma = c(1, 0.1),
                        range.fraction = c(r_bT[1]), 
                        range = r_nbT,
                        sigma.u = 1, sigma.epsilon = 0.2,
                        return.list = TRUE)


df <- df.T$list.field$df
A.data <- df.T$list.field$A.data

#### Stationary model
prior.range.st = c(1, 0.5)
prior.sigma.st = c(1, 0.1)

stk <- inla.stack(data=list(y=df$y), 
                    A=list(A.data, 1),
                    effects=list(s=1:mesh$n, 
                                 intercept=rep(1, nrow(df))), 
                    remove.unused = FALSE, 
                    tag='est')
 
model.stat <- inla.spde2.pcmatern(mesh, 
                                  prior.range = 
                                    c(prior.range.st[1],
                                      prior.range.st[2]),
                                  prior.sigma = 
                                    c(prior.sigma.st[1],
                                      prior.sigma.st[2]))
  
formula.st <- y ~ 0 + intercept + f(s, model=model.stat)
  
res.stationary <- inla(formula.st, data=inla.stack.data(stk),
            control.predictor=list(A = inla.stack.A(stk)),
            family = 'gaussian',
            control.family = list(hyper = list(prec = list(
              prior = "pc.prec", fixed = FALSE, 
              param = c(0.2,0.5)))),
            control.mode=list(restart=T, theta=c(4,-1.7,0.25)))
  
#### Transparent Barrier model with reference correlation not 1
## range fraction optim line 507

x <- 0.4792988
barrier.model <- inla.barrier.pcmatern.plus(mesh, 
                             fem, 
                             barrier.triangles, 
                             prior.range = c(1, 0.5),
                             prior.sigma = c(1, 0.1),
                             range.fraction = c(x[1]))

formula <- y ~ 0 + intercept + f(s, model = barrier.model)

res.barrier <- inla(formula, 
                    data = inla.stack.data(stk),
                    control.predictor = 
                      list(A = inla.stack.A(stk)),
                    family = 'gaussian',
                    control.family = 
                      list(hyper = list(
                          prec = list(prior = "pc.prec", 
                                      fixed = FALSE, 
                                      param = c(0.2,0.5)))),
                    control.mode=list(restart=T, 
                                      theta=c(3.2, 0.4, 1.6)))

res.stationary$summary.hyperpar
exp(res.barrier$summary.hyperpar) 
```

**range for the normal area = 5**

```{r}
r_nbT <- 5
r_bT <- c(0.5) 
df.T <- trans.generate.q2(mesh = mesh, fem = fem, 
                        loc.data = loc.data, 
                        set.inla.seed = 2303, 
                        barrier.triangles = barrier.triangles, 
                        prior.range = c(1, 0.5), prior.sigma = c(1, 0.1),
                        range.fraction = c(r_bT[1]), 
                        range = r_nbT,
                        sigma.u = 1, sigma.epsilon = 0.2,
                        return.list = TRUE)


df <- df.T$list.field$df
A.data <- df.T$list.field$A.data


#### Stationary model
prior.range.st = c(1, 0.5)
prior.sigma.st = c(1, 0.1)

stk <- inla.stack(data=list(y=df$y), 
                    A=list(A.data, 1),
                    effects=list(s=1:mesh$n, 
                                 intercept=rep(1, nrow(df))), 
                    remove.unused = FALSE, 
                    tag='est')
 
model.stat <- inla.spde2.pcmatern(mesh, 
                                  prior.range = 
                                    c(prior.range.st[1],
                                      prior.range.st[2]),
                                  prior.sigma = 
                                    c(prior.sigma.st[1],
                                      prior.sigma.st[2]))
  
formula.st <- y ~ 0 + intercept + f(s, model=model.stat)
  
res.stationary <- inla(formula.st, data=inla.stack.data(stk),
            control.predictor=list(A = inla.stack.A(stk)),
            family = 'gaussian',
            control.family = list(hyper = list(prec = list(
              prior = "pc.prec", fixed = FALSE, 
              param = c(0.2,0.5)))),
            control.mode=list(restart=T, theta=c(4,-1.7,0.25)))
  
#### Transparent Barrier model with reference correlation not 1
## range fraction optim line 507
x <- 0.4792988
barrier.model <- inla.barrier.pcmatern.plus(mesh, 
                             fem, 
                             barrier.triangles, 
                             prior.range = c(1, 0.5),
                             prior.sigma = c(1, 0.1),
                             range.fraction = c(x[1]))

formula <- y ~ 0 + intercept + f(s, model = barrier.model)

res.barrier <- inla(formula, 
                    data = inla.stack.data(stk),
                    control.predictor = 
                      list(A = inla.stack.A(stk)),
                    family = 'gaussian',
                    control.family = 
                      list(hyper = list(
                          prec = list(prior = "pc.prec", 
                                      fixed = FALSE, 
                                      param = c(0.2,0.5)))),
                    control.mode=list(restart=T, 
                                      theta=c(3.2, 0.4, 1.6)))
  
res.stationary$summary.hyperpar
exp(res.barrier$summary.hyperpar) 
```

## Discussion
In this example I am checking the results gotten from different pair of points around the barrier.

However, if I actually wanted to consider more than one pair of points I would have to add a line to the `optim` function such that I find the common r (since it is only one barrier) that minimizes the function for these several pairs. It can't be done with `find.aimed.ratios_` because it assumes there's one $r_b$ for each pair, i.e.  `fem$hdim`-1 has to be equal to the number of different $r_b$. 

Taking more pair of points might make sense in very difficult geometries, where taking a pair of points from one side might actually give different results than taking them on another side. I would evaluate the results taking just one pair at different sides of the barrier and check if it varies too much before trying anything more complex. Code wise it is easy to do, it is just a matter of whether we want to add this option on our implementation or not.

Additionally, using $corr_{nb}$ is much more relevant in this example.

Results from the models obviously depend on the simulated variable response (there's an `rnorm`). In these examples the number of obs is low ($n=20$)








