



Mesh two barrier, i.e. canal

Extend the barrier so it goes to infinity, meaning if the domain is from 2 to 8, the actual mesh goes from 0 to 10

```{r}

```


try with barriers that don't cross the outside boundary
Feb 2
I had a meeting with Havard y Janet on Thursday 6 and we changed things. I wrote a summary on the readme file

range fraction as fraction

i need loc.data, ill just do the gaussian from pre.field. check if i'll use boundaries like poly.water or not 

```{r}
smalldist = 1.5
width = c(4, 4)
#width = c(4, 4)
#max.edge.length = 0.2
max.edge.length = 0.4
n = 50
set.inla.seed = 602
x.mid <- 10
xlim.big <- c(0,20)
xlim.small <- c(3,17)
ylim.big <- c(0,20)
ylim.small <- c(3,17)

poly1 <- local.square.polygon(xlim=c(xlim.big[1]-1, x.mid-smalldist/2), 
                          ylim=x.mid+width[1]*c(-.5, .5))

poly2 <- local.square.polygon(xlim=c(x.mid+smalldist/2, xlim.big[2]+1), 
                          ylim=x.mid+width[2]*c(-.5, .5))

poly.original <- SpatialPolygons(c(poly1@polygons, poly2@polygons))
  
loc1 <- matrix(c(xlim.big[1],ylim.big[1], 
                 xlim.big[2],ylim.big[1], 
                 xlim.big[2],ylim.big[2], 
                 xlim.big[1],ylim.big[2]), 4, 2, byrow = T)
  
seg <- inla.sp2segment(poly.original)
# - Transforms a SpatialPolygon to an "inla polygon"
mesh <- inla.mesh.2d(loc=loc1, 
                     interior = seg, 
                     max.e = max.edge.length, 
                     offset=1)

tl <- length(mesh$graph$tv[,1])
# - the number of triangles in the mesh
posTri <- matrix(0, tl, 2)

for (t in 1:tl){
  temp = mesh$loc[mesh$graph$tv[t, ], ]
  posTri[t,] = colMeans(temp)[c(1,2)] 
}

posTri <- SpatialPoints(posTri)
# - the positions of the triangle centers

bar.original <- over(poly.original, SpatialPoints(posTri), returnList=T)
# - checking which mesh triangles are inside the barrier area
bar.original <- unlist(bar.original)
poly.bar.orginal <- inla.barrier.polygon(mesh, barrier.triangles = bar.original)
# - the Barrier model's polygon
# - in most cases this should be the same as poly.original

# BARRIER 1
bar1 <- over(poly1, SpatialPoints(posTri), returnList=T)
# - checking which mesh triangles are inside the barrier area
bar1 <- unlist(bar1)
poly.bar1 <- inla.barrier.polygon(mesh, barrier.triangles = bar1)
# - the Barrier model's polygon
# - in most cases this should be the same as poly.original

# BARRIER 2
bar2 <- over(poly2, SpatialPoints(posTri), returnList=T)
# - checking which mesh triangles are inside the barrier area
bar2 <- unlist(bar2)
poly.bar2 <- inla.barrier.polygon(mesh, barrier.triangles = bar2)

mat <-  inla.barrier.fem.plus(mesh, list(bar1, bar2)) 
fem <- mat 
barrier.triangles <- list(bar1, bar2)

# PLOTS
poly1_h <- local.square.polygon_T(xlim=c(xlim.small[1], x.mid-smalldist/2), 
                          ylim=x.mid+width[1]*c(-.5, .5))

poly2_h <- local.square.polygon_T(xlim=c(x.mid+smalldist/2, xlim.small[2]), 
                          ylim=x.mid+width[2]*c(-.5, .5))

loc2 <- matrix(c(3,3, 17,3, 17,17, 3,17), 4, 2, byrow = T)

locp2 <- Polygon(loc2, hole = FALSE)
    
poly.water <- SpatialPolygons(list(Polygons(list(locp2, poly1_h, poly2_h), '0')))
poly.water_sf <- st_as_sf(poly.water)
    
set.seed(set.inla.seed)
loc.data <- spsample(x = poly.water, n = n, type = "random")
loc.data_sf <- st_as_sf(loc.data)
loc.data <- loc.data@coords

poly.rect <- SpatialPolygons(list(Polygons(list(poly1_h, poly2_h), '0')))
poly.rect_sf <- st_as_sf(poly.rect)
poly.sq <- SpatialPolygons(list(Polygons(list(locp2), '0')))
poly.sq_sf <- st_as_sf(poly.sq)

sq_bbox <- st_bbox(poly.sq_sf) %>% st_as_sfc()
poly1_bbox <- st_bbox(poly1) %>% st_as_sfc()
poly2_bbox <- st_bbox(poly2) %>% st_as_sfc()
```

Data simulation for Poisson

poly1_h <- local.square.polygon_T(xlim=c(xlim.small[1], x.mid-smalldist/2), 
                          ylim=x.mid+width[1]*c(-.5, .5))

poly2_h <- local.square.polygon_T(xlim=c(x.mid+smalldist/2, xlim.small[2]), 
                          ylim=x.mid+width[2]*c(-.5, .5))

loc2 <- matrix(c(3,3, 17,3, 17,17, 3,17), 4, 2, byrow = T)

locp2 <- Polygon(loc2, hole = FALSE)
    
poly.water <- SpatialPolygons(list(Polygons(list(locp2, poly1_h, poly2_h), '0')))
poly.water_sf <- st_as_sf(poly.water)
    
set.seed(set.inla.seed)
loc.data <- spsample(x = poly.water, n = n, type = "random")
loc.data_sf <- st_as_sf(loc.data)
loc.data <- loc.data@coords

```{r}
poly.win <- SpatialPolygons(list(Polygons(list(locp2, poly1_h, poly2_h), '0')))
    
win <- polyCub::as.owin.SpatialPolygons(poly.win)
#plot(win)
npix <- 10
spatstat.options(npixel = npix)

beta0 <- 0
exp(beta0) * diff(range(win$x)) * diff(range(win$y))

sigma2x <- 0.01
nu <- 1
range.pp <- range
## ----simulapp,eval=TRUE, warning=FALSE, message=FALSE--------------------
set.seed(set.inla.seed)
lg.s <- rLGCP('matern', beta0, var = sigma2x,
              scale = range.pp / sqrt(8), 
              nu = nu, win = win,
              nsim = 50)

## ----xy------------------------------------------------------------------
xy <- cbind(lg.s$`Simulation 15`$x, lg.s$`Simulation 15`$y)
loc.data.pp <- SpatialPoints(xy)
loc.data_sf.pp <- st_as_sf(loc.data.pp)
loc.data.pp <- loc.data.pp@coords
```


```{r}
gg.mesh <- ggplot() + 
  inlabru::gg(mesh) +
  geom_sf(data =poly.rect_sf,
          col='black', alpha=0) + #alpha color inside rect
  geom_sf(data=poly1_bbox, fill=NA, color="red", linewidth = 0.7, linetype = "dashed") +
  geom_sf(data=poly2_bbox, fill=NA, color="red", linewidth = 0.7, linetype = "dashed") +
  geom_sf(data=sq_bbox, fill=NA, color="black", linewidth = 0.7)

gg.mesh.water <- ggplot() +
  inlabru::gg(mesh) +
  geom_sf(data =poly.rect_sf,
          col='black', alpha=1) + #alpha color inside rect
  geom_sf(data=sq_bbox, fill=NA, color="black", linewidth = 0.7) +
  geom_sf(data=poly1_bbox, color="black", linewidth = 0.7) +
  geom_sf(data=poly2_bbox, color="black", linewidth = 0.7) +
  ylim(c(3, 17)) +
  xlim(c(3, 17))

gg.mesh +
  geom_sf(data =loc.data_sf.pp,
          col='black',size=1.7,alpha=0.5)

gg.mesh.water +
  geom_sf(data =loc.data_sf.pp,
          col='black',size=1.7,alpha=0.5)

```

```{r}
#locations, loc.data from rLGCP
nv <- mesh$n
dmesh <- book.mesh.dual(mesh)

#domain.polys <- Polygons(list(Polygon(loc1)), '0')
#domainSP <- SpatialPolygons(list(domain.polys))

domainSP <- locp_sp
# with sf
domainSPsf <- locp_sf
dmesh_sf <- st_as_sf(dmesh) 

# with sapply
w <- sapply(1:length(dmesh), function(i) {
  if (length(st_intersects(dmesh_sf[i, ], domainSPsf)[[1]]) == 1)
    return(st_area(st_intersection(dmesh_sf[i, ], domainSPsf)))
  else {
    return(0)
  }
})

# for w
n <- nrow(xy)
y.pp <- rep(0:1, c(nv, n))
#The exposure vector can be defined as:
e.pp <- c(w, rep(0, n)) 
length(y.pp); length(e.pp)
# The projection matrix is defined in two steps. For the integration points this is just a diagonal matrix because these locations are just the mesh vertices:
imat <- Diagonal(nv, rep(1, nv))
# For the observed points, another projection matrix is defined:
lmat <- inla.spde.make.A(mesh, xy)
# The entire projection matrix is:
A.pp <- rbind(imat, lmat)
# We set up the data stack as follows:
stk.pp <- inla.stack(
  data = list(y = y.pp, e = e.pp), 
  A = list(1, A.pp),
  effects = list(list(b0 = rep(1, nv + n)), list(i = 1:nv)),
  tag = 'pp')
# Results hold
cat('Dimension of A: ', dim(A.pp), '\n')
cat('Dimension of projection matrix: ', dim(imat), '\n')
cat('Number of mesh points: ', mesh$n, '\n')
cat('Number of locations: ', dim(lmat)[1], '\n')
```


## estoy aca, tengo que hacer el stk segun Poisson en transparentbarriermodel line 1215
I think the stack is outside i mean i already di ut and then the formula goes inside. let's see

# Prior: SPDE stationary model
prior.range = c(1, 0.5)
prior.sigma = c(1, 0.1)

#### `c(0.1, 0.1)` aimed ratio  

x <- c(0.11934492, 0.08144928)

barrier.model <- inla.barrier.pcmatern.plus(mesh, 
                             fem, 
                             barrier.triangles, 
                             prior.range = prior.range,
                             prior.sigma = prior.sigma,
                             range.fraction = c(x[1],x[2]))

formula.bm <- y ~ 0 + b0 + f(i, model = barrier.model)
# f(i, model = ...) i instead of s

res.pp.bm <- list(list())

#res.pp.bm[[1]] first set of priors; [[1]][[1]] the first set of aimed ratios
## then, 
## [[1]] set 1: prior.range = c(1, 0.5); prior.sigma = c(1, 0.1)
## [[1]][[1]] set 1, aim c(0.1, 0.1)

res.pp.bm[[1]][[1]] <- inla(formula.bm,
                 data = inla.stack.data(stk.pp),
                 control.predictor = list(A = inla.stack.A(stk.pp)),
                 family = 'poisson', 
                 E = inla.stack.data(stk.pp)$e, 
                 control.inla = list(int.strategy = "eb"))


```{r}
model.tbm.pp <- function(mesh = mesh, 
                      fem = fem, 
                      stk.pp = stk.pp,
                      barrier.triangles = barrier.triangles, 
                      prior.range = c(1, 0.5), prior.sigma = c(1, 0.1),
                      range.fraction = range.fraction,
                      range = range,
                      set.inla.seed = set.inla.seed, # make sure is the same as prev. fx if loc.data = T
                      loc.data = loc.data.pp, 
                      sigma.u = 1, sigma.epsilon = 0.2,
                      poly.original = poly.bar.orginal,
                      prior.range.st = c(1, 0.5),    
                      prior.sigma.st = c(1, 0.1),
                      return.list = TRUE) {
  
  barrier.model <- 
    inla.barrier.pcmatern.plus(mesh, 
                               fem, 
                               barrier.triangles, 
                               prior.range = prior.range,
                               prior.sigma = prior.sigma,
                               range.fraction = range.fraction)

  formula <- y ~ 0 + b0 + f(i, model = barrier.model)
  
  res.pp.bm <- inla(formula,
                 data = inla.stack.data(stk.pp),
                 control.predictor = list(A = inla.stack.A(stk.pp)),
                 family = 'poisson', 
                 E = inla.stack.data(stk.pp)$e, 
                 control.inla = list(int.strategy = "eb"))
  
  #stationary model
  spde <- 
    inla.spde2.pcmatern(mesh, 
                        prior.range = c(prior.range.st[1], prior.range.st[2]),
                        prior.sigma = c(prior.sigma.st[1], prior.sigma.st[2]))

  formula.st <- y ~ 0 + b0 + f(i, model = spde)
  res.pp.st <- inla(formula.st, 
                  family = 'poisson', 
                  data = inla.stack.data(stk.pp), 
                  control.predictor = list(A = inla.stack.A(stk.pp)), 
                  E = inla.stack.data(stk.pp)$e)

  #return list  
  if (return.list == TRUE) {
    
    list.field <- list(barrier.model = barrier.model)
    pos.bm <- list(df = df, res = res.pp.bm)
    pos.st <- list(res = res.pp.st)
    
    return(list(list.field = list.field, pos.bm = pos.bm, pos.st = pos.st))
  }
                     
}

plot.model.tbm.pp <- 
  function(trans, 
           nfrac,
           max.frac = 1,
           left.poly = left.poly,
           poly.bar.orginal = poly.bar.orginal,
           range = range,
           fps = 1,
           set.inla.seed = set.inla.seed,
                              col=alpha('grey', 0),
                              plot.points = points(loc.data, 
                                              pch = 16, 
                                              cex = 0.8, 
                                              col=alpha('gray', 0)),
                              gif.path = "gif/",
                              pal.field = turbo(50),
                              pal.pos.mean = turbo(50),
                              pal.pos.sd = turbo(50),
                              pal.pos.q25 = turbo(50),
                              pal.pos.q50 = turbo(50),
                              pal.pos.q975 = turbo(50),
                              
                              pal.pos.mean.st = turbo(50),
                              pal.pos.sd.st = turbo(50),
                              pal.pos.q25.st = turbo(50),
                              pal.pos.q50.st = turbo(50),
                              pal.pos.q975.st = turbo(50),
                              ...
    ){
#  dir_out_f <- file.path(tempdir(), "truefield_gif")
#  dir.create(dir_out_f, recursive = TRUE)
  
  # barrier model
  dir_out_pm <- file.path(tempdir(), "posmean_gif")
  dir.create(dir_out_pm, recursive = TRUE)
  
  dir_out_sd <- file.path(tempdir(), "possd_gif")
  dir.create(dir_out_sd, recursive = TRUE)
  
  dir_out_q25 <- file.path(tempdir(), "posq25_gif")
  dir.create(dir_out_q25, recursive = TRUE)
  
  dir_out_q5 <- file.path(tempdir(), "posq5_gif")
  dir.create(dir_out_q5, recursive = TRUE)
  
  dir_out_q975 <- file.path(tempdir(), "posq975_gif")
  dir.create(dir_out_q975, recursive = TRUE)
  
  # stationary model
  dir_out_s <- file.path(tempdir(), "statmodel_gif")
  dir.create(dir_out_s, recursive = TRUE)
  
  dir_out_st.sd <- file.path(tempdir(), "st.sd_gif")
  dir.create(dir_out_st.sd, recursive = TRUE)
  
  dir_out_st.q25 <- file.path(tempdir(), "pos.st.q25_gif")
  dir.create(dir_out_st.q25, recursive = TRUE)
  
  dir_out_st.q5 <- file.path(tempdir(), "pos.st.q5_gif")
  dir.create(dir_out_st.q5, recursive = TRUE)
  
  dir_out_st.q975 <- file.path(tempdir(), "pos.st.q975_gif")
  dir.create(dir_out_st.q975, recursive = TRUE)
  
  fr <- (seq(from = left.poly, to = max.frac, length = nfrac)/max.frac)
  if (fr[1] < left.poly) fr[1] <- left.poly

  for (r in 1:length(trans)) {
    
    f <- fr[r]
    range.fraction <- c(left.poly, f)
    
    # SPATIAL FIELD, u
#    fpp <- file.path(dir_out_f, paste0(f, ".png"))
  #  png(fpp)
    
   # local.plot.field(trans[[r]]$list.field$sample, 
     #                main="Spatial posterior for Barrier model",
      #               sub = paste("Barrier Model, range.fraction = c(", 
       #                        range.fraction[1], ", ", range.fraction[2], ")"),
        #             pal = pal.field)
    # plot(poly.bar.orginal, add=T, col = col)
    # plot.points
    # dev.off()
    
    # POSTERIOR MEAN
    fpp <- file.path(dir_out_pm, paste0(f, ".png"))
    png(fpp)
    
    local.plot.field(trans[[r]]$pos.bm$res$summary.random$i$mean, 
                     main="Spatial mean posterior for Barrier model",
                     sub = paste("Barrier Model, range.fraction = c(", 
                               range.fraction[1], ", ", range.fraction[2], ")"),
                     pal = pal.pos.mean)
    plot(poly.bar.orginal, add=T, col = col)
    dev.off()
    
    #POS SD
    fpp <- file.path(dir_out_sd, paste0(f, ".png"))
    png(fpp)
    
    local.plot.field(trans[[r]]$pos.bm$res$summary.random$i$sd, 
                     main="Spatial sd posterior for Barrier model",
                     sub = paste("Barrier Model, range.fraction = c(", 
                               range.fraction[1], ", ", range.fraction[2], ")"),
                     pal = pal.pos.sd)
    plot(poly.bar.orginal, add=T, col = col)
    dev.off()
    
    #POS QUANTILES
    # 0.025
    fpp <- file.path(dir_out_q25, paste0(f, ".png"))
    png(fpp)
    
    local.plot.field(trans[[r]]$pos.bm$res$summary.random$i[,4], 
                     main="Spatial 0.025 quantile posterior for Barrier model",
                     sub = paste("Barrier Model, range.fraction = c(", 
                               range.fraction[1], ", ", range.fraction[2], ")"),
                     pal = pal.pos.q25)
    plot(poly.bar.orginal, add=T, col = col)
    dev.off()

    # 0.5
    fpp <- file.path(dir_out_q5, paste0(f, ".png"))
    png(fpp)
    
    local.plot.field(trans[[r]]$pos.bm$res$summary.random$i[,5], 
                     main="Spatial 0.5 quantile posterior for Barrier model",
                     sub = paste("Barrier Model, range.fraction = c(", 
                               range.fraction[1], ", ", range.fraction[2], ")"),
                     pal = pal.pos.q50)
    plot(poly.bar.orginal, add=T, col = col)
    dev.off()
    
    # 0.975
    fpp <- file.path(dir_out_q975, paste0(f, ".png"))
    png(fpp)
    
    local.plot.field(trans[[r]]$pos.bm$res$summary.random$i[,6], 
                     main="Spatial 0.975 quantile posterior for Barrier model",
                     sub = paste("Barrier Model, range.fraction = c(", 
                               range.fraction[1], ", ", range.fraction[2], ")"),
                     pal = pal.pos.q975)
    plot(poly.bar.orginal, add=T, col = col)
    dev.off()
    
    # SPATIAL ESTIMATE WITH STATIONARY MODEL
    fpp <- file.path(dir_out_s, paste0(f, ".png"))
    png(fpp)
    
    local.plot.field(trans[[r]]$pos.st$res$summary.random$i$mean,
                     main="Spatial estimate with the stationary model",
                     sub = paste("Barrier Model, range.fraction = c(", 
                               range.fraction[1], ", ", range.fraction[2], ")"),
                     pal = pal.pos.mean.st) 
    plot(poly.bar.orginal, add=T, col = col)
    dev.off()
    
    #POS SD st
    fpp <- file.path(dir_out_st.sd, paste0(f, ".png"))
    png(fpp)
    
    local.plot.field(trans[[r]]$pos.st$res$summary.random$i$sd, 
                     main="Spatial sd posterior for Stationary model",
                     sub = paste("Barrier Model, range.fraction = c(", 
                               range.fraction[1], ", ", range.fraction[2], ")"),
                     pal = pal.pos.sd.st)
    plot(poly.bar.orginal, add=T, col = col)
    dev.off()
    
    #POS QUANTILES st
    # 0.025 st
    fpp <- file.path(dir_out_st.q25, paste0(f, ".png"))
    png(fpp)
    
    local.plot.field(trans[[r]]$pos.st$res$summary.random$i[,4], 
                     main="Spatial 0.025 quantile posterior for Stationary model",
                     sub = paste("Barrier Model, range.fraction = c(", 
                               range.fraction[1], ", ", range.fraction[2], ")"),
                     pal = pal.pos.q25.st)
    plot(poly.bar.orginal, add=T, col = col)
    dev.off()

    # 0.5 st
    fpp <- file.path(dir_out_st.q5, paste0(f, ".png"))
    png(fpp)
    
    local.plot.field(trans[[r]]$pos.st$res$summary.random$i[,5], 
                     main="Spatial 0.5 quantile posterior for Stationary model",
                     sub = paste("Barrier Model, range.fraction = c(", 
                               range.fraction[1], ", ", range.fraction[2], ")"),
                     pal = pal.pos.q50.st)
    plot(poly.bar.orginal, add=T, col = col)
    dev.off()
    
    # 0.975 st
    fpp <- file.path(dir_out_st.q975, paste0(f, ".png"))
    png(fpp)
    
    local.plot.field(trans[[r]]$pos.st$res$summary.random$i[,6], 
                     main="Spatial 0.975 quantile posterior for Stationary model",
                     sub = paste("Barrier Model, range.fraction = c(", 
                               range.fraction[1], ", ", range.fraction[2], ")"),
                     pal = pal.pos.q975.st)
    plot(poly.bar.orginal, add=T, col = col)
    dev.off()
  }
  
    ## bm
    # SPATIAL FIELD, u
    
    # POSTERIOR MEAN
    image_write(image = image_animate(
      image_join(
        lapply(list.files(dir_out_pm, full.names = TRUE), image_read)), 
      fps = fps), 
      path = paste0(gif.path, "pos.mean.gif"))
    
    #POS SD
    image_write(image = image_animate(
      image_join(
        lapply(list.files(dir_out_sd, full.names = TRUE), image_read)), 
      fps = fps), 
      path = paste0(gif.path, "pos.sd.gif"))
    
    #POS QUANTILES
    # 0.025
    image_write(image = image_animate(
      image_join(
        lapply(list.files(dir_out_q25, full.names = TRUE), image_read)), 
      fps = fps), 
      path = paste0(gif.path, "pos.q25.gif"))
    
    # 0.5
    image_write(image = image_animate(
      image_join(
        lapply(list.files(dir_out_q5, full.names = TRUE), image_read)), 
      fps = fps), 
      path = paste0(gif.path, "pos.q5.gif"))
    
    # 0.975
    image_write(image = image_animate(
      image_join(
        lapply(list.files(dir_out_q975, full.names = TRUE), image_read)), 
      fps = fps), 
      path = paste0(gif.path, "pos.q975.gif"))
    
    ## st
    # u
    image_write(image = image_animate(
      image_join(
        lapply(list.files(dir_out_s, full.names = TRUE), image_read)), 
      fps = fps), 
      path = paste0(gif.path, "stat.rnadom.mean.gif"))
    
    # st sd
    image_write(image = image_animate(
      image_join(
        lapply(list.files(dir_out_st.sd, full.names = TRUE), image_read)), 
      fps = fps), 
      path = paste0(gif.path, "pos.sd.st.gif"))
    
    #POS QUANTILES st
    # 0.025
    image_write(image = image_animate(
      image_join(
        lapply(list.files(dir_out_st.q25, full.names = TRUE), image_read)), 
      fps = fps), 
      path = paste0(gif.path, "pos.q25.st.gif"))
    
    # 0.5
    image_write(image = image_animate(
      image_join(
        lapply(list.files(dir_out_st.q5, full.names = TRUE), image_read)), 
      fps = fps), 
      path = paste0(gif.path, "pos.q5.st.gif"))
    
    # 0.975
    image_write(image = image_animate(
      image_join(
        lapply(list.files(dir_out_st.q975, full.names = TRUE), image_read)), 
      fps = fps), 
      path = paste0(gif.path, "pos.q975.st.gif"))
    
    
    unlink(dir_out_pm, recursive = T)
    unlink(dir_out_sd, recursive = T)
    unlink(dir_out_q25, recursive = T)
    unlink(dir_out_q5, recursive = T)
    unlink(dir_out_q975, recursive = T)
    unlink(dir_out_s, recursive = T)
    unlink(dir_out_st.sd, recursive = T)
    unlink(dir_out_st.q25, recursive = T)
    unlink(dir_out_st.q5, recursive = T)
    unlink(dir_out_st.q975, recursive = T)
}

```

```{r}
range = 4
nfrac = 5
max.frac = 10
left.poly = 0.01
left.poly.c <- 0.01
right.poly.c <- 3

fr <- (seq(from = left.poly, 
          to = max.frac, 
          length = nfrac)/max.frac) 
tbm.frac.pp <- list()

if (fr[1] < left.poly) fr[1] <- left.poly
for (r in 1:2) { #
  f <- fr[r]
}
  range.fraction <- c(left.poly, f)
  tbm.frac.pp[[1]] <- model.tbm.pp(mesh = mesh, fem = fem,
              stk.pp = stk.pp,                   
              barrier.triangles = barrier.triangles,
              prior.range = c(1, 0.5), prior.sigma = c(1, 0.1),  
              range.fraction = c(left.poly, f),
              range = range,
              set.inla.seed = set.inla.seed, 
              loc.data = loc.data.pp, 
              sigma.u = 1, sigma.epsilon = 0.2,
              poly.original = poly.bar.orginal,
              prior.range.st = c(1, 0.5),
              prior.sigma.st = c(1, 0.1),
              return.list = TRUE)


trans <- tbm.frac.pp

plot.model.tbm.pp(tbm.frac.pp, 
           nfrac,
           max.frac = max.frac,
           left.poly = 0.01,
           poly.bar.orginal = poly.bar.orginal,
           range = range,
           fps = 1)

```





```{r}
bm_hp <- list()
st_hp <- list()
frac = 5

bm_hp <- rbind(
data.frame(exp(trans[[1]]$pos.bm$res$summary.hyperpar[3,c(1,3,5)])),
data.frame(exp(trans[[2]]$pos.bm$res$summary.hyperpar[3,c(1,3,5)])),
data.frame(exp(trans[[3]]$pos.bm$res$summary.hyperpar[3,c(1,3,5)])),
data.frame(exp(trans[[4]]$pos.bm$res$summary.hyperpar[3,c(1,3,5)])),
data.frame(exp(trans[[5]]$pos.bm$res$summary.hyperpar[3,c(1,3,5)])))
st_hp <- rbind(
data.frame((trans[[1]]$pos.st$res$summary.hyperpar[2,c(1,3,5)])),
data.frame((trans[[2]]$pos.st$res$summary.hyperpar[2,c(1,3,5)])),
data.frame((trans[[3]]$pos.st$res$summary.hyperpar[2,c(1,3,5)])),
data.frame((trans[[4]]$pos.st$res$summary.hyperpar[2,c(1,3,5)])),
data.frame((trans[[5]]$pos.st$res$summary.hyperpar[2,c(1,3,5)])))

colnames(bm_hp)[2:3] <- c("0.025quant", "0.975quant")
rownames(bm_hp) <- c("r1", "r2", "r3", "r4","r5")

colnames(st_hp)[2:3] <- c("0.025quant", "0.975quant")
rownames(st_hp) <- c("r1", "r2", "r3", "r4","r5")
#write.csv(rbind(bm_hp,st_hp), "4proposal\\trans2.5.csv")
#bm_hp.25 = bm_hp 
#st_hp.25 = st_hp
```

```{r}
ggplot() + 
  inlabru::gg(mesh.seg) +
  geom_sf(data =poly.rect_sf,
          col='black', alpha=0) + #alpha color inside rect
  geom_sf(data=poly1_bbox, fill=NA, color="red", linewidth = 0.7, linetype = "dashed") +
  geom_sf(data=poly2_bbox, fill=NA, color="red", linewidth = 0.7, linetype = "dashed") +
  geom_sf(data=sq_bbox, fill=NA, color="black", linewidth = 0.7)

ggplot() + 
  inlabru::gg(mesh.seg) +
  geom_sf(data =poly.rect_sf,
          col='black', alpha=1) + #alpha color inside rect
  geom_sf(data=sq_bbox, fill=NA, color="black", linewidth = 0.7) +
  geom_sf(data=poly1_bbox, color="black", linewidth = 0.7) +
  geom_sf(data=poly2_bbox, color="black", linewidth = 0.7) +
  ylim(c(3, 17)) +
  xlim(c(3, 17)) 
```


# MESH wiht almost triangular barriers
mesh.seg_h <- inla.mesh.2d(boundary = poly.water, #? has to have holes=F
                           interior = seg, 
                           max.e = max.edge.length, 
                           offset=1)
ggplot() + 
  inlabru::gg(mesh.seg_h)


```{r}
#store_w <- w
#w <- store_w
#sum(w)
#table(w>0); table(w==0)

pal <- wes_palette("Zissou1")
colr = rep(c(pal[2]), length = as.numeric(length(w)))
colr[w>0] = pal[5]
plot(dmesh, col = colr)

par(mar = c(2, 2, 1, 1), mgp = 2:0)
plot(mesh$loc, asp = 1, col = (w == 0) + 1, pch = 19, xlab = '', ylab = '') 
plot(dmesh, add = TRUE)
lines(loc1, col = 3)
```

```{r}
locp1 <- Polygon(loc1, hole = FALSE)
#Polygon(poly1@polygons[[1]]@Polygons[[1]]@coords, hole = TRUE)
poly.win <- SpatialPolygons(list(Polygons(list(locp1, 
                                               Polygon(poly1@polygons[[1]]@Polygons[[1]]@coords, hole = TRUE),
                                               Polygon(poly2@polygons[[1]]@Polygons[[1]]@coords, hole = TRUE)), 
                                          '0')))
win <- polyCub::as.owin.SpatialPolygons(poly.win)
npix <- 2
spatstat.options(npixel = npix)

beta0 <- 0
exp(beta0) * diff(range(win$x)) * diff(range(win$y))

sigma2x <- 0.01
nu <- 1
range.pp <- range
## ----simulapp,eval=TRUE, warning=FALSE, message=FALSE--------------------
set.seed(set.inla.seed)
lg.s <- rLGCP('matern', beta0, var = sigma2x,
              scale = range.pp / sqrt(8), 
              nu = nu, win = win)

## ----xy------------------------------------------------------------------
xy <- cbind(lg.s$x, lg.s$y)
xy <- xy[(which(xy[,1] < 17 & xy[,1] > 3)),]
xy <- xy[(which(xy[,2] < 17 & xy[,2] > 3)),]

#!which(xy[,1] < 15 & xy[,1] > 5)
dim(xy)
loc.data.pp <- SpatialPoints(xy)
loc.data_sf.pp <- st_as_sf(loc.data.pp)
loc.data.pp <- loc.data.pp@coords

gg.mesh +
  geom_sf(data =loc.data_sf.pp,
          col='black',size=1.7,alpha=0.5)

gg.mesh.water +
  geom_sf(data =loc.data_sf.pp,
          col='black',size=1.7,alpha=0.5)

```
