 
### Example 5 (ex5)   

Spatial domain: rectangle
Barrier: circle

```{r}
rxy <- c(12, 12)
set.inla.seed <- 2303
n <- 20
max.edge.length = 0.4

circle <- cbind(
  cos(seq(0, 2*pi, length=50)) * 2 + 0.50 * rxy[1], 
  sin(seq(0, 2*pi, length=50)) * 2 + 0.5 * rxy[2])

poly <- Polygon(circle, hole = FALSE)
poly1 <- SpatialPolygons(list(Polygons(list(poly), ID = runif(1))))

poly.original <- SpatialPolygons(c(poly1@polygons))

loc1 <- matrix(c(0,0, 10,0, 0,10, 10,10), 4, 2, byrow = T)

seg <- inla.sp2segment(poly1)
# - Transforms a SpatialPolygon to an "inla polygon"
mesh <- inla.mesh.2d(loc=loc1, interior = seg, 
                    max.e = max.edge.length, offset=1)

tl <- length(mesh$graph$tv[,1])
# - the number of triangles in the mesh
posTri <- matrix(0, tl, 2)

for (t in 1:tl){
  temp = mesh$loc[mesh$graph$tv[t, ], ]
  posTri[t,] = colMeans(temp)[c(1,2)] 
}

posTri <- SpatialPoints(posTri)
# - the positions of the triangle centers

bar.original <- over(poly.original, SpatialPoints(posTri), returnList=T)
# - checking which mesh triangles are inside the barrier area
bar.original <- unlist(bar.original)
poly.bar.orginal <- inla.barrier.polygon(mesh, barrier.triangles = bar.original)
# - the Barrier model's polygon
# - in most cases this should be the same as poly.original

# BARRIER 1
bar1 <- over(poly1, SpatialPoints(posTri), returnList=T)
# - checking which mesh triangles are inside the barrier area
bar1 <- unlist(bar1)
poly.bar1 <- inla.barrier.polygon(mesh, barrier.triangles = bar1)
# - the Barrier model's polygon
# - in most cases this should be the same as poly.original

# PLOTS
mat <-  inla.barrier.fem.plus(mesh, list(bar1))

poly1_h <- Polygon(circle, hole = TRUE)

loc1 <- matrix(c(2,2, 10,2, 10,10, 2,10), 4, 2, byrow = T)

locp <- Polygon(loc1, hole = FALSE)
    
poly.water <- SpatialPolygons(list(Polygons(list(locp, poly1_h), '0')))

poly.water_sf <- st_as_sf(poly.water)
    
set.seed(set.inla.seed)
loc.data <- spsample(x = poly.water, n = n, type = "random")
loc.data_sf <- st_as_sf(loc.data)
loc.data <- loc.data@coords
    
mesh_h <-inla.mesh.2d(boundary = poly.water_sf,
                      max.e = max.edge.length, offset=1)
    
range = 2
fem <- mat
barrier.triangles <- list(bar1)
zlim = c(0.1, 1)
xlim = poly.water@bbox[1, ] 
ylim = poly.water@bbox[2, ]

proj = inla.mesh.projector(mesh, xlim = xlim, 
                           ylim = ylim, dims=c(300, 300))

ggplot(data = poly.water_sf) + 
      inlabru::gg(mesh_h) + #plot mesh_hb alternatively
      geom_sf(data =loc.data_sf,
          col='purple',size=1.7,alpha=0.5) 
```
#### Choose two pair of points

One for each block with different r

```{r}
width <- 4
y.mid <- 6
y.up <- y.mid + (width/2)
y.low <- y.mid - (width/2)

location <- matrix(c(c(6, 4), rep(y.mid, 2)), ncol = 2)
```

```{r}
# upper pair of points

max.edge.length = 0.4
  
A <- list()
A[[1]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[1,1],y.up), nrow=1, ncol=2))
A[[2]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[1,1],(y.up + max.edge.length/2)), nrow=1, ncol=2))
A[[3]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[1,1],(y.up + max.edge.length)), nrow=1, ncol=2))

id.nodeA <- c()
id.nodeA[1] = which.max(A[[1]][1, ])
id.nodeA[2] = which.max(A[[2]][1, ])
id.nodeA[3] = which.max(A[[3]][1, ])

# just to check the coordinates and compare to the plot above
data.frame(x = c(mesh$loc[id.nodeA[1], 1], mesh$loc[id.nodeA[2], 1], mesh$loc[id.nodeA[3], 1]),
           y = c(mesh$loc[id.nodeA[1], 2], mesh$loc[id.nodeA[2], 2], mesh$loc[id.nodeA[3], 2]))

A.y.vector <- c(mesh$loc[id.nodeA[[1]],][2],
                  mesh$loc[id.nodeA[[2]],][2],
                  mesh$loc[id.nodeA[[3]],][2])

A.tmp <- A[[which(A.y.vector > y.up)[1]]]
id.node <- id.nodeA[which(A.y.vector > y.up)[1]]
id.coord <- c(mesh$loc[id.node, 1], mesh$loc[id.node, 2])
return.list.up <- list(A.tmp = A.tmp, id.coord = id.coord, id.node = id.node)

## lower point, i.e. point in barrier area
A <- list()
A[[1]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[1,1],y.up), nrow=1, ncol=2))
A[[2]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[1,1],(y.up - max.edge.length/2)), nrow=1, ncol=2))
A[[3]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(location[1,1],(y.up - max.edge.length)), nrow=1, ncol=2))
id.nodeA <- c()
id.nodeA[1] = which.max(A[[1]][1, ])
id.nodeA[2] = which.max(A[[2]][1, ])
id.nodeA[3] = which.max(A[[3]][1, ])

A.y.vector <- c(mesh$loc[id.nodeA[[1]],][2],
                  mesh$loc[id.nodeA[[2]],][2],
                  mesh$loc[id.nodeA[[3]],][2])

A.tmp <- A[[which(A.y.vector < (y.up-0.01))[1]]]
id.node <- id.nodeA[which(A.y.vector < (y.up-0.01))[1]]
id.coord <- c(mesh$loc[id.node, 1], mesh$loc[id.node, 2])

return.list.low <- list(A.tmp = A.tmp, id.coord = id.coord, id.node = id.node)

return.list <- list(normal.point = return.list.up, barrier.point = return.list.low)

coord.df_norm <- return.list$normal.point$id.coord
coord.df_bar <- return.list$barrier.point$id.coord

points_nb <- rbind(coord.df_norm, coord.df_bar)
rownames(points_nb) <- NULL
colnames(points_nb) <- c("x", "y")
points_nb <- as.matrix(points_nb)
poly_nb <- Polygon(points_nb)
SpatialPoints(poly_nb@coords)

sp_points_nb <- SpatialPoints(poly_nb@coords)
sf_points_nb <- st_as_sf(sp_points_nb)

ggplot(data = poly.water_sf) + 
      inlabru::gg(mesh) + #plot mesh_hb alternatively
      geom_sf(data =sf_points_nb,
          col='purple',size=1.7,alpha=0.5) 

ggplot(data = poly.water_sf) + 
      inlabru::gg(mesh) +
  geom_sf(data =sf_points_nb,
          col='purple',size=1.7,alpha=0.5) +
  ylim(c(6,8.5)) +
  xlim(c(4,8))

#left are upper points, move through y
return.list.left <- return.list
coord.df_norm.left <- coord.df_norm
coord.df_bar.left <- coord.df_bar
```

```{r}
## pair of points on the side of the circle
x.r <- 4
A <- list()
A[[1]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(x.r, location[2,2]), nrow=1, ncol=2))
A[[2]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c((x.r + max.edge.length/2), location[2,2]), nrow=1, ncol=2))
A[[3]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c((x.r + max.edge.length), location[2,2]), nrow=1, ncol=2))

id.nodeA <- c()
id.nodeA[1] = which.max(A[[1]][1, ])
id.nodeA[2] = which.max(A[[2]][1, ])
id.nodeA[3] = which.max(A[[3]][1, ])

# just to check the coordinates and compare to the plot above
data.frame(x = c(mesh$loc[id.nodeA[1], 1], mesh$loc[id.nodeA[2], 1], mesh$loc[id.nodeA[3], 1]),
           y = c(mesh$loc[id.nodeA[1], 2], mesh$loc[id.nodeA[2], 2], mesh$loc[id.nodeA[3], 2]))

A.x.vector <- c(mesh$loc[id.nodeA[[1]],][1],
                  mesh$loc[id.nodeA[[2]],][1],
                  mesh$loc[id.nodeA[[3]],][1])

A.tmp <- A[[which(A.x.vector > (x.r+0.01))[1]]]
id.node <- id.nodeA[which(A.x.vector > (x.r+0.01))[1]]
id.coord <- c(mesh$loc[id.node, 1], mesh$loc[id.node, 2])
#list up is x inside barrier
return.list.up <- list(A.tmp = A.tmp, id.coord = id.coord, id.node = id.node)

## left point, i.e. normal area point
A <- list()
A[[1]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c(x.r, location[2,2]), nrow=1, ncol=2))
A[[2]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c((x.r - max.edge.length/2), location[2,2]), nrow=1, ncol=2))
A[[3]] <- inla.spde.make.A(mesh=mesh,
                     loc = matrix(c((x.r - max.edge.length), location[2,2]), nrow=1, ncol=2))
id.nodeA <- c()
id.nodeA[1] = which.max(A[[1]][1, ])
id.nodeA[2] = which.max(A[[2]][1, ])
id.nodeA[3] = which.max(A[[3]][1, ])

# just to check the coordinates and compare to the plot above
data.frame(x = c(mesh$loc[id.nodeA[1], 1], mesh$loc[id.nodeA[2], 1], mesh$loc[id.nodeA[3], 1]),
           y = c(mesh$loc[id.nodeA[1], 2], mesh$loc[id.nodeA[2], 2], mesh$loc[id.nodeA[3], 2]))

A.x.vector <- c(mesh$loc[id.nodeA[[1]],][1],
                  mesh$loc[id.nodeA[[2]],][1],
                  mesh$loc[id.nodeA[[3]],][1])

A.tmp <- A[[which(A.x.vector < x.r)[1]]]
id.node <- id.nodeA[which(A.x.vector < x.r)[1]]
id.coord <- c(mesh$loc[id.node, 1], mesh$loc[id.node, 2])

return.list.low <- list(A.tmp = A.tmp, id.coord = id.coord, id.node = id.node)

###
return.list <- list(normal.point = return.list.low, barrier.point = return.list.up)

coord.df_norm <- return.list$normal.point$id.coord
coord.df_bar <- return.list$barrier.point$id.coord

points_nb <- rbind(coord.df_norm, coord.df_bar)
rownames(points_nb) <- NULL
colnames(points_nb) <- c("x", "y")
points_nb <- as.matrix(points_nb)
poly_nb <- Polygon(points_nb)
SpatialPoints(poly_nb@coords)

sp_points_nb <- SpatialPoints(poly_nb@coords)
sf_points_nb <- st_as_sf(sp_points_nb)

ggplot(data = poly.water_sf) + 
      inlabru::gg(mesh) + #plot mesh_hb alternatively
      geom_sf(data =sf_points_nb,
          col='purple',size=1.7,alpha=0.5) 

ggplot(data = poly.water_sf) + 
      inlabru::gg(mesh) +
  geom_sf(data =sf_points_nb,
          col='purple',size=1.7,alpha=0.5) +
  ylim(c(4,8)) +
  xlim(c(2,6))

# right are points on the side, move through x
return.list.right <- return.list
coord.df_norm.right <- coord.df_norm
coord.df_bar.right <- coord.df_bar
```

#### corr.from.Q function for two (or more) rb's

I need to calculate correlation for two points now, so pass a vector to solve instead of one Inode

```{r}
id.node <- list()
id.coord <- list()
in.id.node <- list()

id.node[[1]] = return.list.left$normal.point$id.node
id.coord[[1]] = return.list.left$normal.point$id.coord
in.id.node[[1]] = return.list.left$barrier.point$id.node
```

#### optim

```{r}
nb.model <- function(rbs, #rbs number of r_b
                     id.node = id.node, 
                     in.id.node = in.id.node) { 
  
  nb.model <- inla.barrier.pcmatern.plus(mesh, 
                             fem, 
                             barrier.triangles, 
                             prior.range,
                             prior.sigma,
                             range.fraction = rep(1, rbs))
  
  Q.nb <- inla.rgeneric.q(nb.model, "Q", 
                          theta = c(log(prior.sigma[1]), log(prior.range[1])))
  
  corr.nb <- 
    corr.from.Q.alltogether(Q = Q.nb,
                            id.node = id.node,
                            in.id.node = in.id.node)
  
  return(list(nb.model = nb.model, Q = Q.nb, corr = corr.nb))
}


find.aimed.ratios_ <- function(x, 
                               aimed.ratio,
                               corr.nb) {
  
  barrier.model <- inla.barrier.pcmatern.plus(
    mesh = mesh,
    fem = fem,
    barrier.triangles = barrier.triangles,
    prior.range = prior.range,
    prior.sigma = prior.sigma,
    range.fraction = x)
  
  Q <- inla.rgeneric.q(
    barrier.model, 
    "Q",
    theta = c(log(prior.sigma[1]), 
              log(prior.range[1])))
  
  corr.bm <- corr.from.Q.alltogether(
    Q = Q, 
    id.node = id.node, 
    in.id.node = in.id.node)
  
  corr <- c()
  for (i in seq_along(corr.bm)) {
    corr[i] <- corr.bm[[i]]/corr.nb[[i]]
  }
  
  A <- diag(aimed.ratio)
  B <- diag(corr)
  M <- A-B
  mini <- norm(M, "F")
  
  return(mini)
}
```


```{r}
prior.range = c(1, 0.5)
prior.sigma = c(1, 0.1)
rb <- c(0.1)
x <- rb
aim <- c(0.5)
find.aimed.ratios(x, aimed.ratio = aim)
  
  
  



```



```{r}
prior.range = c(1, 0.5)
prior.sigma = c(1, 0.1)
rb <- c(0.1)
x <- rb
aim <- c(0.1)

corr.ref <- nb.model(rbs = 1, id.node = id.node, in.id.node = in.id.node)$corr

find.aimed.ratios_(x, aimed.ratio = aim, corr.nb = list(1,1)) == find.aimed.ratios(x, aimed.ratio = aim) # TRUE, 0.813839

find.aimed.ratios_(x, aimed.ratio = aim, corr.nb = corr.ref) # 0.8582385
```



```{r}
aim = 0.1
## with corr nb = 1
par = rep(0.5, length(aim))
optim(par = par, find.aimed.ratios_, 
      aimed.ratio = aim, corr.nb = list(1),
      method="L-BFGS-B",
      lower = c(0.01, 0.01), 
      upper = c(1,1))
```

$par
[1] 0.5

$value
[1] 0

$counts
function gradient 
       1        1 

$convergence
[1] 0

$message
[1] "CONVERGENCE: NORM OF PROJECTED GRADIENT <= PGTOL"

$par: [1] 0.1174683 0.1075167
$value: [1] 1.300353e-05
$counts: function gradient 
      41       41 
$convergence: [1] 0
$message: [1] "CONVERGENCE: REL_REDUCTION_OF_F <= FACTR*EPSMCH"

```{r}
## with corr nb = corr.ref
corr.ref <- nb.model(rbs = 2, id.node = id.node, in.id.node = in.id.node)$corr
optim(par = par, find.aimed.ratios_, 
      aimed.ratio = aim, corr.nb = corr.ref,
      method="L-BFGS-B",
      lower = c(0.01, 0.01), 
      upper = c(1,1))
```

$par: [1] 0.1157458 0.1071045
$value: [1] 1.781817e-06
$counts: function gradient 
      30       30 
$convergence: [1] 0
$message: [1] "CONVERGENCE: REL_REDUCTION_OF_F <= FACTR*EPSMCH"

#### Barrier model considering the prev. results

Comparison barrier model and stationary model, using the range fraction obtained from `optim` for the barrier model.

##### Simulate response variable

```{r}
r_nbT <- 2
r_bT <- c(0.1, 0.1) 
df.T <- trans.generate.q2(mesh = mesh, fem = fem, 
                        loc.data = loc.data, 
                        set.inla.seed = 1702, 
                        barrier.triangles = barrier.triangles, 
                        prior.range = c(2, 0.5), prior.sigma = c(1, 0.1),
                        range.fraction = c(r_bT[1],r_bT[2]), 
                        range = r_nbT,
                        sigma.u = 1, sigma.epsilon = 0.2,
                        return.list = TRUE)


df <- df.T$list.field$df
A.data <- df.T$list.field$A.data
```

##### Stationary model

```{r}
prior.range.st = c(1, 0.5)
prior.sigma.st = c(1, 0.1)

stk <- inla.stack(data=list(y=df$y), 
                    A=list(A.data, 1),
                    effects=list(s=1:mesh$n, 
                                 intercept=rep(1, nrow(df))), 
                    remove.unused = FALSE, 
                    tag='est')
 
model.stat <- inla.spde2.pcmatern(mesh, 
                                  prior.range = 
                                    c(prior.range.st[1],
                                      prior.range.st[2]),
                                  prior.sigma = 
                                    c(prior.sigma.st[1],
                                      prior.sigma.st[2]))
  
formula.st <- y ~ 0 + intercept + f(s, model=model.stat)
  
res.stationary <- inla(formula.st, data=inla.stack.data(stk),
            control.predictor=list(A = inla.stack.A(stk)),
            family = 'gaussian',
            control.family = list(hyper = list(prec = list(
              prior = "pc.prec", fixed = FALSE, 
              param = c(0.2,0.5)))),
            control.mode=list(restart=T, theta=c(4,-1.7,0.25)))
  
res.stationary$summary.hyperpar
```
##### Transparent Barrier model with reference correlation not 1

```{r}
## range fraction optim line 323
x <- c(0.1157458, 0.1071045)
barrier.model <- inla.barrier.pcmatern.plus(mesh, 
                             fem, 
                             barrier.triangles, 
                             prior.range = c(1, 0.5),
                             prior.sigma = c(1, 0.1),
                             range.fraction = c(x[1],x[2]))

formula <- y ~ 0 + intercept + f(s, model = barrier.model)

res.barrier <- inla(formula, 
                    data = inla.stack.data(stk),
                    control.predictor = 
                      list(A = inla.stack.A(stk)),
                    family = 'gaussian',
                    control.family = 
                      list(hyper = list(
                          prec = list(prior = "pc.prec", 
                                      fixed = FALSE, 
                                      param = c(0.2,0.5)))),
                    control.mode=list(restart=T, 
                                      theta=c(3.2, 0.4, 1.6)))
  
exp(res.barrier$summary.hyperpar) 
```

### Discussion

Results from the model are similar, however the confidence interval for the range hyperparameter in the Transparent Barrier model is narrower.








