
# Dugong Example

## Data

```{r}
# https://www.flaticon.com/
dng_icon <- "dng.data/dugong.png"

bathym_ <- raster("dng.data/RSPbathym100m.tif")
crs_longlat <- CRS("+proj=longlat +datum=WGS84")
crs_km <- CRS("+proj=utm +zone=39 ellps=WGS84 +units=km")
bathym_longlat <- projectRaster(bathym_, crs = crs_longlat)
bathym_km <- projectRaster(bathym_, crs = crs_km)

# Data for all species from helicopter surveys.
Data_allspp <- readRDS("dng.data/RSP_survey_sightings.rds")
# Data Incidental Sightings Dugongs
Data_ISD <- readRDS("dng.data/incidental_sightings_dugongs.rds")

# Data for the 10 different species. 
# The list number corresponds to sppID, e.g. species 7 is spp[[7]]
spp_ <- 10
spp <- list()
for (s in 1:spp_) {
  data <- Data_allspp %>% filter(sp_grp_nam == paste0("spp", as.character(s)))
  spp[[s]] <- data
}

# Dugong = spp7
Data_7spp <- spp[[7]]

# bind ISD with Survey helicopter data
# Dugong is the only one that has data coming from 2 sources.
Data_ISD_ <- dplyr::select(Data_ISD, c(Lat, Long, geometry)) %>% 
  rename(lat = Lat, long = Long) %>% 
  mutate(method = "ISD")

spp7 <- dplyr::select(Data_7spp, c(lat, long, geometry)) %>% 
  mutate(method = "Survey")

all_dugong <- rbind(Data_ISD_, spp7)
st_crs(Data_ISD_)
Data_ISD <- st_transform(Data_ISD_, crs_km)
cords_Dng.xy <- st_coordinates(Data_ISD)
cords_Dng.sp <- SpatialPoints(cords_Dng.xy, proj4string = crs_km)
```

```{r}
# line 15 "mybath"
# creating polygons with terra
bathym <- terra::rast(bathym_longlat)
plot(bathym)
bathym_poly <- terra::as.polygons(bathym > -Inf)
plot(bathym_poly)
# getting coordinates for all the polygons
cords <- terra::crds(bathym)
# getting bathymetry values for all polygons
vals <- terra::extract(bathym, as.data.frame(cords))
# create df with cords and bathym values.
df_bath <- cbind(as.data.frame(cords), vals) %>% rename(bathymetry = layer)
# filter polygons corresponding to islands and sand patches, select x, y ordinates.
sea_cords <- df_bath %>% dplyr::filter(bathymetry <= -2) %>% dplyr::select(x,y)
island_cords <- df_bath %>% dplyr::filter(bathymetry > -2) %>% dplyr::select(x,y)
```

```{r}
# boundary of the study area:
# raster w/o the boundary
raster_study.area <- bathym_longlat
raster_study.area[raster_study.area < -500] <- NA
# opposite
raster_deep.sea<- bathym_longlat
raster_deep.sea[raster_deep.sea>= -500] <- NA
# plot
plot(raster_study.area); plot(raster_deep.sea)

# raster w/o islands
# islands have r = 0.01
raster_no.islands <- raster_study.area
raster_no.islands[raster_no.islands >= 0] <- NA # create raster with NA values for islands.
# opposite
# boundary and islands have range = 0.01
raster_islands <- bathym_longlat
raster_islands[raster_islands < 0 & raster_islands >= -500] <- NA 
# plot
plot(raster_no.islands); plot(raster_islands)
raster_b1 <- raster_islands

# raster w/o islands (b1) and b2 
# 90% between -10 and 0 depth, https://www.nature.com/articles/s41598-021-04412-3
# ratio = 0.1/0.9 ~ 0.11
raster_no.b2 <- raster_no.islands
raster_no.b2[raster_no.b2 < -10] <- NA
# opposite
raster_b2 <- raster_no.islands
raster_b2[raster_b2 >= -10] <- NA
# plot
plot(raster_no.b2); plot(raster_b2)
```

```{r}
# from terra lib
# SpatRaster
spatr_no.island <- terra::rast(raster_no.islands)
# SpatVector
spatvect_no.island <- terra::as.polygons(spatr_no.island > -Inf) # bathym_poly
#SpatialPolygonsDataFrame 
spdf.water <- as(spatvect_no.island, "Spatial") # bathym_sp_df
# for the mesh I need b2 without NA

# There's one observation that is out of the bathymetry map
spdf.water@bbox
Data_ISD <-
Data_ISD %>% filter(long > spdf.water@bbox[1,1] &long < spdf.water@bbox[1,2] 
                    &lat > spdf.water@bbox[2,1] &lat < spdf.water@bbox[2,2])
# data inside the mesh box                  
cords_Dng.xy <- st_coordinates(Data_ISD)
cords_Dng.sp <- SpatialPoints(cords_Dng.xy, proj4string = crs_km)


sp4msh <- spTransform(spdf.water, crs_km)
spdf.water <- sp4msh

max.edge.length <- 2
bound.outer <- diff(range(cords_Dng.xy[,1]))/3
mesh.dng <- inla.mesh.2d(boundary = sp4msh,
                    max.edge = c(1,5)*max.edge.length,
                    cutoff = 0.05,
                    offset = c(max.edge.length, bound.outer))
plot(mesh.dng)
mesh.dng$crs <- crs_km
```

```{r}
sf4msh <- st_as_sf(sp4msh)
mesh.dng_sf <- inla.mesh.2d(boundary = sf4msh,
                            max.edge = c(1,5)*max.edge.length,
                            cutoff = 0.05,
                            offset = c(max.edge.length, bound.outer))
mesh.dng_sf$crs <- crs_km

gg_mesh <- ggplot() +
  inlabru::gg(mesh.dng_sf, crs = crs_km) +
  coord_sf(crs = crs_km) +
  geom_sf(data=st_as_sf(cords_Dng.sp),
          col='purple',size=1.7,alpha=0.5)
gg_mesh
```

```{r}
# Spatial polygons for barrier 1 = islands, poly1
spatr.b1 <- terra::rast(raster_b1)
spatv.b1 <- terra::as.polygons(spatr.b1 > -Inf) # bathym_poly
spdf.b1_ <- as(spatv.b1, "Spatial") 
spdf.b1 <- spTransform(spdf.b1_, crs_km)

sp.b1_ <- geometry(spdf.b1)
n.spb1 <- length(sp.b1_@polygons[[1]]@Polygons)
idx.spb1 <- seq(1:n.spb1)
sea_list = lapply(idx.spb1, function(n) Polygon(sp.b1_@polygons[[1]]@Polygons[[n]]@coords, hole = F)) 

sp.b1 <- SpatialPolygons(list(Polygons(sea_list, ID = runif(1)))) #poly1

# Spatial polygons for barrier 2, between -10 and -500, poly2
spatr.b2 <- terra::rast(raster_b2)
spatv.b2 <- terra::as.polygons(spatr.b2 > -Inf) # bathym_poly
spdf.b2_ <- as(spatv.b2, "Spatial") 
spdf.b2 <- spTransform(spdf.b2_, crs_km)

sp.b2_ <- geometry(spdf.b2)
n.spb2 <- length(sp.b2_@polygons[[1]]@Polygons)
idx.spb2 <- seq(1:n.spb2)
sea_list2 = lapply(idx.spb2, function(n) Polygon(sp.b2_@polygons[[1]]@Polygons[[n]]@coords, hole = F)) 
sp.b2 <- SpatialPolygons(list(Polygons(sea_list2, ID = runif(1)))) #poly2

sp.bars <- SpatialPolygons(c(sp.b1@polygons, sp.b2@polygons)) #poly.original
```

```{r}
# BARRIER TRIANGLES
tl <- length(mesh.dng$graph$tv[,1])
# - the number of triangles in the mesh.pp
posTri <- matrix(0, tl, 2)

for (t in 1:tl){
    temp = mesh.dng$loc[mesh.dng$graph$tv[t, ], ]
    posTri[t,] = colMeans(temp)[c(1,2)] 
}

posTri <- SpatialPoints(posTri)

# - the positions of the triangle centers
bars.centers <- over(sp.bars, SpatialPoints(posTri), returnList=T)
# - checking which mesh.dng triangles are inside the barrier area
bars.centers <- unlist(bars.centers) #bar.original
poly.bars <- inla.barrier.polygon(mesh.dng, barrier.triangles = bars.centers)
# - the Barrier model's polygon
# - in most cases this should be the same as poly.original

# BARRIER 1
bar1 <- over(sp.b1, SpatialPoints(posTri), returnList=T)
# - checking which mesh.dng triangles are inside the barrier area
bar1 <- unlist(bar1)
poly.bar1 <- inla.barrier.polygon(mesh.dng, barrier.triangles = bar1)

# BARRIER 2
bar2 <- over(sp.b2, SpatialPoints(posTri), returnList=T)
# - checking which mesh.dng triangles are inside the barrier area
bar2 <- unlist(bar2)
poly.bar2 <- inla.barrier.polygon(mesh.dng, barrier.triangles = bar2)

fem <-  inla.barrier.fem.plus(mesh.dng, list(bar1, bar2))

barrier.triangles <- list(bar1, bar2)

plot(mesh.dng_sf, main="Mesh and Omega")
plot(st_as_sf(poly.bars), add=T, col='lightblue')
```

```{r}
dmesh <- book.mesh.dual(mesh.dng)

domainSP <- sp4msh
domainSPsf <- st_as_sf(domainSP)
dmesh_sf <- st_as_sf(dmesh) 
st_crs(dmesh_sf) <- crs_km
# st_crs<- : replacing crs does not reproject data; use st_transform for that

# with sapply
w <- sapply(1:length(dmesh), function(i) {
  if (length(st_intersects(dmesh_sf[i, ], domainSPsf)[[1]]) == 1)
    return(st_area(st_intersection(dmesh_sf[i, ], domainSPsf)))
  else {
    return(0)
  }
})

#store_w <- w
#w <- store_w
sum(w)
table(w>0); table(w==0)

pal <- wes_palette("Zissou1")
colr = rep(c(pal[2]), length = as.numeric(length(w)))
colr[w>0] = pal[5]
plot(dmesh, col = colr)
```

## Projection matrices

```{r}
n <- nrow(cords_Dng.xy)
nv <- mesh.dng$n
xy <- cords_Dng.xy
xy.sp <- cords_Dng.sp

y.pp <- rep(0:1, c(nv, n))
#The exposure vector can be defined as:
e.pp <- c(w, rep(0, n)) 
length(y.pp); length(e.pp)
# The projection matrix is defined in two steps. For the integration points this is just a diagonal matrix because these locations are just the mesh vertices:
imat <- Diagonal(nv, rep(1, nv))
# For the observed points, another projection matrix is defined:
lmat <- inla.spde.make.A(mesh.dng, xy.sp)
# The entire projection matrix is:
A.pp <- rbind(imat, lmat)

# We set up the data stack as follows:
stk.pp <- inla.stack(
  data = list(y = y.pp, e = e.pp), 
  A = list(1, A.pp),
  effects = list(list(b0 = rep(1, nv + n)), list(i = 1:nv)),
  tag = 'pp')

# Results hold
cat('Dimension of A: ', dim(A.pp), '\n')
cat('Dimension of projection matrix: ', dim(imat), '\n')
cat('Number of mesh points: ', mesh.dng$n, '\n')
cat('Number of locations: ', dim(lmat)[1], '\n')
```
Stationary SPDE model

The prior for the hyper-parameter $r$ is calibrated to have a median around half of the study area
and $\sigma_u$ is chosen in order to have probability 0.01 to have values greater than 1.

```{r}
# 0.5*diff(range(cords_Dng.xy[,2])) = 40.94401
prior.range <- c(10, .5)
prior.sigma <- c(3, 0.01)

spde <- inla.spde2.pcmatern(mesh = mesh.dng,
  prior.range = prior.range,
  prior.sigma = prior.range) 

formula.st <- y ~ 0 + b0 + f(i, model = spde)

res.pp.st <- inla(formula.st, 
                  family = 'poisson', 
                  data = inla.stack.data(stk.pp), 
                  control.predictor = list(A = inla.stack.A(stk.pp)), 
                  E = inla.stack.data(stk.pp)$e)

res.pp.st$summary.hyperpar
```


```{r}
range.marginal.st <- as.data.frame(
  cbind(
    rep("st", nrow(inla.tmarginal(function(x) x, 
                                  res.pp.st$marginals.hyperpar[[1]]))),
    inla.tmarginal(function(x) x, res.pp.st$marginals.hyperpar[[1]])))

colnames(range.marginal.st)[1] <- c("model")

range.marginal.st  <- range.marginal.st %>% 
  dplyr::mutate(range = as.numeric(x), density = as.numeric(y))

ggplot(data = range.marginal.st , aes(x = range, y = density, color = model)) +
  geom_line() +
  ggsci::scale_color_ucscgb() +
  xlab("range") +
  ylab("density")
```


```{r}
range.marginal <- cbind(
    rep("st", nrow(inla.tmarginal(function(x) x, 
                                  res.pp.st$marginals.hyperpar[[1]]))),
    rep("range", nrow(inla.tmarginal(function(x) x, 
                                  res.pp.st$marginals.hyperpar[[1]]))),
    inla.tmarginal(function(x) x, res.pp.st$marginals.hyperpar[[1]]))

b0.marginal <- cbind(
    rep("st", nrow(res.pp.st$marginals.fixed[[1]])),
    rep("b0", nrow(res.pp.st$marginals.fixed[[1]])),
    res.pp.st$marginals.fixed[[1]])

sigma.marginal <- cbind(
    rep("st", nrow(inla.tmarginal(function(x) x, 
                                  res.pp.st$marginals.hyperpar[[2]]))),
    rep("sigma", nrow(inla.tmarginal(function(x) x, 
                                  res.pp.st$marginals.hyperpar[[2]]))),
    inla.tmarginal(function(x) x, res.pp.st$marginals.hyperpar[[2]]))

marginal.st <- as.data.frame(
  rbind(range.marginal, b0.marginal, sigma.marginal)
)


colnames(range.marginal.st)[1] <- c("model")

range.marginal.st  <- range.marginal.st %>% 
  dplyr::mutate(range = as.numeric(x), density = as.numeric(y))

ggplot(data = range.marginal.st , aes(x = range, y = density, color = model)) +
  geom_line() +
  ggsci::scale_color_ucscgb() +
  xlab("range") +
  ylab("density") 


marginal.st <- as.data.frame(
  cbind(
    rep("st", nrow(inla.tmarginal(function(x) x, 
                                  res.pp.st$marginals.hyperpar[[1]]))),
    inla.tmarginal(function(x) x, res.pp.st$marginals.hyperpar[[1]])))

colnames(marginal.st)[1:2] <- c("model", "par")

marginal.st  <- marginal.st %>% 
  dplyr::mutate(val = as.numeric(x), density = as.numeric(y)) %>% 
  dplyr::select(!c(x, y))

df <- marginal.st %>% dplyr::filter(par == "range")
gg.range.st <- 
ggplot(data = df , aes(x = val, y = density, color = model)) +
  geom_line() +
  ggsci::scale_color_ucscgb() +
  xlab("range") +
  ylab("density") 

df <- marginal.st %>% dplyr::filter(par == "b0")
gg.b0.st <-
ggplot(data = df , aes(x = val, y = density, color = model)) +
  geom_line() +
  ggsci::scale_color_ucscgb() +
  xlab("b0") +
  ylab("density") 

df <- marginal.st %>% dplyr::filter(par == "sigma")
gg.sigma.st <-
ggplot(data = df , aes(x = val, y = density, color = model)) +
  geom_line() +
  ggsci::scale_color_ucscgb() +
  xlab("sigma") +
  ylab("density") 

gridExtra::grid.arrange(gg.range.st, gg.b0.st, gg.sigma.st, nrow = 3, ncol = 1)
```


from res.pp.st
*** max_correction = 25.01 >= 25.00, so 'vb.correction' is aborted
	*** Please (re-)consider your model, priors, confounding, etc.
	*** You can change the emergency value (current value=25.00) by 
	*** 	'control.inla=list(control.vb=list(emergency=...))'
	
```{r}
res.pp.st$summary.hyperpar
```


```{r}

```

I dont know if I need it
```{r}
poly.water <- spdf.water 
zlim = c(0.1, 1)
xlim = poly.water@bbox[1, ] 
ylim = poly.water@bbox[2, ]

proj = inla.mesh.projector(mesh.dng, xlim = xlim, 
                           ylim = ylim, dims=c(300, 300))

#PLOT
poly.water_sf <- st_as_sf(poly.water)
coast_bbox <- st_bbox(poly.water_sf) %>% st_as_sfc()

poly.bars_sf <- st_as_sf(poly.bars)

poly.bar1_sf <- st_as_sf(poly.bar1)
poly.bar2_sf <- st_as_sf(poly.bar2)


```






```{r}

```


```{r 2, eval=FALSE, echo=FALSE}
plot1 <- leaflet() %>% 
  setView(lng = median(Data_ISD$long), lat = median(Data_ISD$lat), zoom = 8) %>%
  addProviderTiles(providers$OpenStreetMap, group = "Open Street Map") %>% 
  # Add additional basemap layers
  addProviderTiles(providers$Esri.WorldImagery, group = "ESRI World Imagery") %>% 
  addProviderTiles(providers$Esri.OceanBasemap, group = "ESRI Ocean Basemap") %>% 
  # Add a User-Interface (UI) control to switch layers
  addLayersControl(
    baseGroups = c("Open Street Map","ESRI World Imagery","ESRI Ocean Basemap"),
    options = layersControlOptions(collapsed = FALSE)) 

frameWidget(plot1, width = "100%", height = "500")
```

```{r 3}
plot_dng1 <- leaflet() %>% 
  setView(lng = mean(Data_ISD$long), lat = mean(Data_ISD$lat), zoom = 8) %>%
  addProviderTiles(providers$OpenStreetMap, group = "Open Street Map") %>% 
  # Add additional basemap layers
  addProviderTiles(providers$Esri.WorldImagery, group = "ESRI World Imagery") %>% 
  addProviderTiles(providers$Esri.OceanBasemap, group = "ESRI Ocean Basemap") %>% 
  # Add a User-Interface (UI) control to switch layers
  addLayersControl(
    baseGroups = c("Open Street Map","ESRI World Imagery","ESRI Ocean Basemap"),
    options = layersControlOptions(collapsed = FALSE)) %>%
  addMarkers(lng = Data_ISD$long, lat = Data_ISD$lat, group = "Dugong",
             icon = 
               list(iconUrl = dng_icon,
                    iconSize = c(20,20)))

frameWidget(plot_dng1, width = "100%", height = "500")
```




Functions
These are different than the ones in functions.rmd so update and change for local.plot.field_ when I finish so there's no 2 fx with the same name

```{r}
# from: https://haakonbakkagit.github.io/btopic103.html
local.plot.field = function(field, xlim, ylim, mesh, pal = plasma(17), ...){
  if (missing(xlim)) xlim = c(2, 8) 
  if (missing(ylim)) ylim = xlim
  proj = inla.mesh.projector(mesh, xlim = xlim, 
                             ylim = ylim, dims=c(300, 300))
  # - Can project from the mesh onto a 300x300 grid 
  #   for plots
  field.proj = inla.mesh.project(proj, field)
  # - Do the projection
  # pal <- wes_palette("Zissou1", type = "continuous")
  image.plot(list(x = proj$x, y=proj$y, z = field.proj), 
             xlim = xlim, ylim = ylim, col = pal, ...)  
  # - Use image.plot to get nice colors and legend
}
# print(mesh$n)
```


```{r}
# pp has if(missing(xlim))...
local.plot.fieldpp = function(field, mesh, poly.water, xlim, ylim, zlim=c(0.1, 1), dims=c(300, 300),...){ #, pal = rainbow(17)
 # poly.water = km_sp4msh, it has to be the SpatialPolygon object used in inla.mesh.2d
 # Error when using the wrong mesh
 stopifnot(length(field) == mesh$n)
    
 # Choose plotting region to be the same as the study area polygon
 if (missing(xlim)) xlim = poly.water@bbox[1, ] 
 if (missing(ylim)) ylim = poly.water@bbox[2, ]
    
 # Project the mesh onto a 300x300 grid   
 proj = inla.mesh.projector(mesh, xlim = xlim,                              
                            ylim = ylim, dims=c(300, 300)) 
 # Do the projection 
 field.proj = inla.mesh.project(proj, field)
       
 # Plot it
 image.plot(list(x = proj$x, y=proj$y, z = field.proj), 
               xlim = xlim, ylim = ylim, zlim = zlim, ...)  #, col = pal
  }
```

```{r}
#Plot barrier model
local.find.correlation = function(Q, location, mesh) {
  ## Vector of standard deviations
  sd = sqrt(diag(inla.qinv(Q)))
  
  ## Create a fake A matrix, to extract the closest mesh node index
  A.tmp = inla.spde.make.A(mesh=mesh, 
                           loc = matrix(c(location[1],location[2]),1,2))
  
  ## Index of the closest node
  id.node = which.max(A.tmp[1, ])
  
  
  print(paste('The location used was c(', 
              round(mesh$loc[id.node, 1], 4), ', ', 
              round(mesh$loc[id.node, 2], 4), ')' ))
  
  ## Solve a matrix system to find the column of the covariance matrix
  Inode = rep(0, dim(Q)[1]) 
  Inode[id.node] = 1
  covar.column = solve(Q, Inode)
  # compute correaltions
  corr = drop(matrix(covar.column)) / (sd*sd[id.node])
  return(corr)
}
```







